### 2021-07-09 submission/submission.tex
create document

% !TeX spellcheck = en_US
\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{OcamlPro - Fabrice Le Fessant et Thomas Sibut-Pinote}
\title{Groth16 zkSNARK Proof Verification : Three Use Cases}
\begin{document}
\maketitle
In this submission, we propose three different use cases for Groth16
zkSNARK proofs on the FreeTON blockchain.

\section{Technical contribution to the usability: `ft`}

(justifié parce que les jurés peuvent se servir de `ft` pour tester
notre code)

\section{A toy example: Sudoku}
\label{section_sudoku}

Let's start with our first toy use case. Suppose you want to set up a Sudoku problem for your students to solve, so that upon completion they receive some token. The issue is that once any student has solved it, the solution sits on the blockchain for all to see. All the other students can cheat by copying it, instead of doing the work by themselves, which defeats the whole purpose.

\section{A better example: Project Euler}
\label{section_euler}

The previous example is somewhat limited by the fact that sudokus are easily solvable problems, either by hand or with a computer; they are not a realistic use case of zk-snarks. Let's keep the idea of a decentralized classroom. the famous website Project Euler\footnote{{https://projecteuler.net/}} offers math and programming problems of various difficulty to its users. It uses captchas to prevent brute force attempts at guessing the answer to a problem. The answers to problems are stored statically on its servers and the answers are checked against them. Can we make Project Euler decentralized? Using the idea from Section \ref{section_sudoku}, we can prevent users from stealing others' solutions \textbf{and} from brute-forcing them, due to the cost of generating proofs.

\section{A useful example: SetCodeMultisigWallet with a pin code}
\label{section_pincode}

\end{document}

### 2021-07-10 03_pincode/cpp/main.cpp
non working version of 03_pincode

@@ -1,0 +1,447 @@
+//---------------------------------------------------------------------------//
+// Copyright (c) 2018-2021 Mikhail Komarov <nemo@nil.foundation>
+//
+// Licensed under the Apache License, Version 2.0 (the "License");
+// you may not use this file except in compliance with the License.
+// You may obtain a copy of the License at
+//
+//    http://www.apache.org/licenses/LICENSE-2.0
+//
+// Unless required by applicable law or agreed to in writing, software
+// distributed under the License is distributed on an "AS IS" BASIS,
+// WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+// See the License for the specific language governing permissions and
+// limitations under the License.
+//---------------------------------------------------------------------------//
+
+#include <iostream>
+
+#include <boost/filesystem.hpp>
+#include <boost/program_options.hpp>
+
+#include "detail/r1cs_examples.hpp"
+#include "detail/sha256_component.hpp"
+
+#include <nil/crypto3/algebra/curves/bls12.hpp>
+#include <nil/crypto3/algebra/fields/bls12/base_field.hpp>
+#include <nil/crypto3/algebra/fields/bls12/scalar_field.hpp>
+#include <nil/crypto3/algebra/fields/arithmetic_params/bls12.hpp>
+#include <nil/crypto3/algebra/curves/params/multiexp/bls12.hpp>
+#include <nil/crypto3/algebra/curves/params/wnaf/bls12.hpp>
+
+#include <nil/crypto3/zk/components/blueprint.hpp>
+#include <nil/crypto3/zk/components/blueprint_variable.hpp>
+
+#include <nil/crypto3/zk/snark/schemes/ppzksnark/r1cs_gg_ppzksnark.hpp>
+#include <nil/crypto3/zk/snark/schemes/ppzksnark/r1cs_gg_ppzksnark/marshalling.hpp>
+
+#include <nil/crypto3/zk/snark/algorithms/generate.hpp>
+#include <nil/crypto3/zk/snark/algorithms/verify.hpp>
+#include <nil/crypto3/zk/snark/algorithms/prove.hpp>
+
+#include <nil/crypto3/zk/components/component.hpp>
+
+#include <nil/crypto3/zk/components/blueprint.hpp>
[…]

### 2021-07-10 submission/submission.tex

@@
 \usepackage{graphicx}
+\usepackage{hyperref}
+\hypersetup{
+	colorlinks=true,
+	linkcolor=blue,
+	filecolor=magenta,
+	urlcolor=gray
+}
+
+\usepackage{xcolor}
+\usepackage{listings}
+
+\lstdefinestyle{BashInputStyle}{
+	language=bash,
+	basicstyle=\small\sffamily,
+	columns=fullflexible,
+%	backgroundcolor=\color{yellow!20},
+	linewidth=0.9\linewidth,
+	xleftmargin=0.1\linewidth
+}
+
 \author{OcamlPro - Fabrice Le Fessant et Thomas Sibut-Pinote}
-\title{Groth16 zkSNARK Proof Verification : Three Use Cases}
+\title{Groth16 zkSNARK Proof Verification on Freeton : Three Use Cases}
+
 \begin{document}
 \maketitle
+
+The present document is an official submission to the 18$^{\text{th}}$ contest\footnote{\url{https://devex.gov.freeton.org/proposal?proposalAddress=0\%3Ae6b65075478e7d412fdb0870452f30dfa8bf51272e28a3167abc5c5df6fd051d}} of the DevEx governance.
+Although we accepted earlier to be part of the jury, we understand that by submitting this document we waive our right to vote in the present contest.
+
 In this submission, we propose three different use cases for Groth16
@@
 
-\section{Technical contribution to the usability: `ft`}
+\section{Technical contribution to the usability of ZkSnark-enabled Freeton with `ft`}
 
-(justifié parce que les jurés peuvent se servir de `ft` pour tester
-notre code)
+In the course of participating in this contest, we were led to refine our in-house tools in order to more easily manipulate the Nil Foundation forks of the Ton Virtual Machine (TVM), the TON Solidity compiler and the TVM linker.
+
+The freeton wallet \lstinline|ft| can be installed using Docker (\url{https://ocamlpro.github.io/freeton_wallet/sphinx/install.html#using-docker}) or \lstinline|opam|.
+
+Once it is installed, a Zksnark-ready sandbox can be installed by simply running:
+
+\begin{lstlisting}[style=BashInputStyle]
+ft switch create sandbox --image ocamlpro/nil-local-node
+\end{lstlisting}
+
+Now all commands from the \lstinline|ft| documentation will work, in particular it will be easy to create accounts, deploy contracts, and call them as seen in \url{https://ocamlpro.github.io/freeton_wallet/sphinx/use-cases.html}.
 
@@
 All the other students can cheat by copying it, instead of doing the work by themselves, which defeats the whole purpose.
+One other advantage is that we don't need to implement the whole logic of the computation on the smart contract.
+For some size of Sudoku, this is probably worthwhile.
 
@@
 Let's keep the idea of a decentralized classroom.
-the famous website Project Euler\footnote{{https://projecteuler.net/}} offers math and programming problems of various difficulty to its users.
+the famous website Project Euler\footnote{\url{https://projecteuler.net/}} offers math and programming problems of various difficulty to its users.
 It uses captchas to prevent brute force attempts at guessing the answer to a problem.
@@
 
+Our final example is much more practical.
+What happens when one loses the private key controlling one's wallet?
+One solution, on a multisig wallet, is to have e.g.
+two private keys, one being safely stored in a vault at the bank.
+But what if going to the bank is impossible?
+Another solution is to enable a one-time pin code to change the public key controlling a given wallet.
+
+This solution needs to be zero-knowledge because any solution that lets attackers observe the pin code in the clear gives them an opportunity to intercept it (for instance if they are a validator) and change the order of transactions, to gain control of the wallet.
+
+Our solution consists in providing a zero-knowledge proof of the pin code \emph{tied} with the new public key (to avoid interception of the proof).
+
 \end{document}

### 2021-07-11 03_pincode/cpp/main.cpp
Update submission.tex and pincode contracts

@@ -163,8 +163,6 @@ void build_circuit ( blueprint<field_type> &bp, std::vector<uint32_t> &passphras
   blueprint_variable<field_type> public_pubkey3;
   public_pubkey3.allocate( bp );
 
-  bp.set_input_sizes(4);
-
   blueprint_variable<field_type> secret_pubkey0;
   secret_pubkey0.allocate( bp );
 
@@ -188,6 +186,8 @@ void build_circuit ( blueprint<field_type> &bp, std::vector<uint32_t> &passphras
 
   blueprint_variable<field_type> secret_hash3;
   secret_hash3.allocate( bp );
+  
+  bp.set_input_sizes(4);
 
   // This sets up the blueprint variables
   // so that the first one (out) represents the public
@@ -261,13 +261,58 @@ void use_circuit( std::string passphrase, std::string pubkey ){
   cerr << "(3)" << endl ;
 
   blueprint<field_type> bp;
+  
+  blueprint_variable<field_type> public_pubkey0;
+  public_pubkey0.allocate( bp );
 
-  // Normally, here, we would load the bp from files 'provkey.bin' and 'verifkey.bin'
-#ifndef PROVING_KEY_SERIALIZER
-  build_circuit( bp, passphrase32 );
-#else
-  exit(2) ; // TODO
-#endif
+  blueprint_variable<field_type> public_pubkey1;
+  public_pubkey1.allocate( bp );
+
+  blueprint_variable<field_type> public_pubkey2;
+  public_pubkey2.allocate( bp );
+
+  blueprint_variable<field_type> public_pubkey3;
+  public_pubkey3.allocate( bp );
+
+  blueprint_variable<field_type> secret_pubkey0;
+  secret_pubkey0.allocate( bp );
+
+  blueprint_variable<field_type> secret_pubkey1;
+  secret_pubkey1.allocate( bp );
+
+  blueprint_variable<field_type> secret_pubkey2;
+  secret_pubkey2.allocate( bp );
+
+  blueprint_variable<field_type> secret_pubkey3;
+  secret_pubkey3.allocate( bp );
+
+  blueprint_variable<field_type> secret_hash0;
+  secret_hash0.allocate( bp );
+
+  blueprint_variable<field_type> secret_hash1;
+  secret_hash1.allocate( bp );
+
[…]

### 2021-07-11 submission/submission.tex

--- 2021-07-09 submission/submission.tex
@@
 \usepackage{graphicx}
+\usepackage{hyperref}
+\hypersetup{
+	colorlinks=true,
+	linkcolor=blue,
+	filecolor=magenta,
+	urlcolor=gray
+}
+
+\usepackage{xcolor}
+\usepackage{listings}
+
+\lstdefinestyle{BashInputStyle}{
+	language=bash,
+	basicstyle=\small\sffamily,
+	columns=fullflexible,
+%	backgroundcolor=\color{yellow!20},
+	linewidth=0.9\linewidth,
+	xleftmargin=0.1\linewidth
+}
+
 \author{OcamlPro - Fabrice Le Fessant et Thomas Sibut-Pinote}
-\title{Groth16 zkSNARK Proof Verification : Three Use Cases}
+\title{Groth16 zkSNARK Proof Verification on Freeton : Three Use Cases}
+
 \begin{document}
 \maketitle
+
+The present document is an official submission to the 18$^{\text{th}}$
+contest\footnote{\url{https://devex.gov.freeton.org/proposal?proposalAddress=0\%3Ae6b65075478e7d412fdb0870452f30dfa8bf51272e28a3167abc5c5df6fd051d}}
+of the DevEx governance: {\em Groth16 zkSNARK Proof Verification Use
+  Cases}. Although we accepted earlier to be part of the jury, we
+understand that by submitting this document we waive our right to vote
+in the present contest.
+
 In this submission, we propose three different use cases for Groth16
-zkSNARK proofs on the FreeTON blockchain.
+zkSNARK proofs on the FreeTON blockchain:
+\begin{itemize}
+\item Sudoky: Zksnarks are used to prove that the user has a solution
+  to a given Sudoky problem, without providing the solutions to other
+  users ;
+\item Euler Project: Zksnarks are used to prove that the user has
+  found the solution to an Euler problem ;
+\item Pin-code reset of forgotten keys: Zksnarks are used to replace a
+  pubkey when the user has lost his secret key
+\end{itemize}
 
-\section{Technical contribution to the usability: `ft`}
-
-(justifié parce que les jurés peuvent se servir de `ft` pour tester
-notre code)
+Finally, we finish this document by a section showing the
+contributions that we did for the Free TON community while working on
+this contest.
 
@@
 
-\section{A useful example: SetCodeMultisigWallet with a pin code}
+\section{Pin code reset for forgotten keys}
 \label{section_pincode}
 
+In this use case, we use Zksnarks to allow users to replace their
+public keys in multisig wallets. The typical use is when a user has
+lost the associated secret key, and is unable to sign/confirm any new
+transaction. With our approach, the user first creates a recovery
+contract, where a passphrase is associated to his public key. If he
+needs to change his public key, he can use Zksnarks to associate a new
+public key in his recovery contract, and tell multisig wallets to
+safely replace his pubkey by the new one.
+
+Compared to other approaches, this use can provide several
+improvements:
+\begin{itemize}
+\item The user does not disclose his passphrase. Most other approaches
+  (based on hashes for example) give an opportunity for
+  man-in-the-middle attacks ;
+\item As the user does not disclose his passphrase, the pubkey can be
+  replaced several times ;
+\item The user does not need to create the new public key ahead of
+  time. Instead, he can create it when he has lost the former one,
+  decreasing the likelihood of losing the associated secret key also ;
+\end{itemize}
+
+\subsection{Technical solution}
+
+This use case includes 3 different components:
+\begin{description}
+\item[PinCode Client:] it is a C++ program linked to the Blueprint
+  Zksnarks library. It can be used in two different ways:
+  \begin{itemize}
+  \item To create the initial circuit using the passphrase. The client
+    should be called as:
+\begin{verbatim}
+pincode-client prepare "my pass phrase"
+\end{verbatim}
+   This will generate a file \lstinline{verifkey.hex} that can be used
+   as an argument when deploying the \lstinline{PubkeyRecovery} smart
+   contract, and a file \lstinline{provkey.hex} that can be used to
+   create new witnesses ;
+ \item To create a witness that the passphrase is known when providing
+   a new public key. Because the witness contains the new public key,
+   an attacker cannot intercept the message and replace it. The client
+   should be called as:
+\begin{verbatim}
+pincode-client prove "my pass phrase" "PUBKEY_AS_HEX_NUMBER"
+\end{verbatim}
+  The command expects to find the file \lstinline{provkey.hex} and
+  generates a file \lstinline{proof.hex} that should be submitted to
+  the \lstinline{PubkeyRecovery} smart contract together with the new
+  public key.
+  \end{itemize}
+\item[PubkeyRecovery smart contract:] This smart contract is a TIP-3
+  contract, using the initial public key to verify its address. This
+  contract is very simple. It contains:
+  \begin{itemize}
+  \item A constructor to set the circuit that will be used to verify
+    that the passphrase is known when it is used ;
+  \item An external function
+    \lstinline{SetNewPubkey(bytes proof, uint256 pubkey)}
+    to define the new public key, while providing a
+    proof of knowledge of the passphrase ;
+  \item An external function
+    \lstinline{RecoverPubkey(address multisigaddr)}
+    to call a multisig contract to update the
+    corresponding custodian. The multisig contract will verify that
+    the address is correct before replacing the public key ;
+  \end{itemize}
+\item[Modified Multisig Wallet:] This is a standard multisig wallet,
+  modified to recognize addresses of \lstinline{PubkeyRecovery} smart
+  contracts. They provide two additionnal functions:
+  \begin{itemize}
+  \item An external function
+    \lstinline{SetPubkeyRecoveryCode(TvmCell code)}
+    to define the code of the \lstinline{PubkeyRecovery} smart
+    contract. Because the code hash is known, anybody can call this
+    function with the correct code.
+  \item An external function
+    \lstinline{RecoverPubkey(uint256 oldkey, uint256 newkey)}
+    that can only be called by a
+    \lstinline{PubkeyRecovery} smart contract.
+  \end{itemize}
+\end{description}
+
+\section{Contributions to the Free TON community}
+
+In the course of participating to this contest, we were led to refine
+our in-house tools in order to more easily manipulate the Nil
+Foundation forks of the Ton Virtual Machine (TVM), the TON Solidity
+compiler and the TVM linker.
+
+Our first contribution is a public Docker image containing the TONOS
+SE compiled with Zksnarks support. The image is published as {\tt
+  ocamlpro/nil-local-node} and is built from
+\url{https://github.com/NilFoundation/tonos-se}.
+
+Running it is simple:
+\begin{verbatim}
+docker run -d --name local-node -e USER_AGREEMENT=yes -p80:80 ocamlpro/nil-local-node
+\end{verbatim}
+
+Another way to use it is through our development tool {\tt ft}, a Free
+TON Wallet designed for developers:
+\url{https://github.com/OCamlPro/freeton_wallet}
+
+For this contest, a set of improvements has been contributed to {\tt
+  ft} to ease using it.
+
+In particular:
+\begin{itemize}
+\item The interface has been improved to provide multiple levels of
+  subcommands, making them easier to understand and to use ;
+\item A new argument {\tt --image} is available with {\tt ft switch
+  create} to specify the Docker image to use. This new argument is
+  specially useful for our Docker image for NilFoundation TONOS SE.
+\end{itemize}
+
+As a consequence, a Zksnark-ready sandbox (local network) can be
+installed by simply running:
+
+\begin{lstlisting}[style=BashInputStyle]
+ft switch create sandbox --image ocamlpro/nil-local-node
+\end{lstlisting}
+
+Now all commands from the \lstinline|ft| documentation will work, in
+particular it will be easy to create accounts, deploy contracts, and
+call them as seen in
+\url{https://ocamlpro.github.io/freeton_wallet/sphinx/use-cases.html}.
+
+The Docker image of \lstinline|ft| has been updated to use
+NilFoundation tools
+(\lstinline|solc|, \lstinline|tonos-cli|, \lstinline|tvm_linker|), it is
+the easiest way to use \lstinline|ft| if you don't want to build
+it. See the installation instruction at
+(\url{https://ocamlpro.github.io/freeton_wallet/sphinx/install.html#using-docker}).
+
 \end{document}

### 2021-07-12 03_pincode/cpp/build.sh
Add build.sh in 03_pincode/cpp

@@ -1,0 +1,34 @@
+#!/bin/sh
+
+if [ -f picosha2.h ]; then
+    echo Error: you should rename picosha2.h to picosha2.hpp
+    echo Only sources with .hpp and .cpp are supported
+    exit 2
+fi
+
+
+CURDIR=$(pwd)
+FILES=$(ls *.hpp *.cpp)
+
+ROOTDIR=$(cd ../..; pwd)
+
+cd $ROOTDIR
+if [ ! -f ton-proof-verification-contest/CMakeLists.txt ]; then
+    git clone --recursive https://github.com/NilFoundation/ton-proof-verification-contest.git
+fi
+
+cd ton-proof-verification-contest
+if [ ! -f build/Makefile ]; then
+  mkdir build
+  cd build
+  cmake ..
+fi
+
+for file in $FILES; do
+    ln -sf $CURDIR/$file bin/cli/src/$file
+done
+
+cd build
+make cli
+
+

### 2021-07-12 03_pincode/cpp/main.cpp

@@ -14,6 +14,9 @@
 // limitations under the License.
 //---------------------------------------------------------------------------//
 
+#define PROVING_KEY_FILE "provkey.bin"
+#define VERIFICATION_KEY_FILE "verifkey.bin"
+
 #include <iostream>
 
 #include <boost/filesystem.hpp>
@@ -54,12 +57,11 @@ using namespace nil::crypto3::algebra;
 
 #include <iostream>
 #include <string>
-#include "picosha2.h"
+#include "picosha2.hpp"
 using namespace std;
 
 typedef algebra::curves::bls12<381> curve_type;
 typedef typename curve_type::scalar_field_type field_type;
-
 typedef zk::snark::r1cs_gg_ppzksnark<curve_type> scheme_type;
 
 using std::string;
@@ -232,17 +234,17 @@ void prepare_circuit ( std::string passphrase ){
   cerr << "(4)" << endl ;
 
   std::vector<std::uint8_t> proving_key_byteblob = nil::marshalling::verifier_input_serializer_tvm<scheme_type>::process( keypair.first );
-  binfile_of_byteblob( "provkey.bin", proving_key_byteblob );
+  binfile_of_byteblob( PROVING_KEY_FILE, proving_key_byteblob );
   hexfile_of_byteblob( "provkey.hex", proving_key_byteblob );
 
   std::vector<std::uint8_t> verification_key_byteblob = nil::marshalling::verifier_input_serializer_tvm<scheme_type>::process( keypair.second );
 
-  binfile_of_byteblob( "verifkey.bin", verification_key_byteblob );
+  binfile_of_byteblob( VERIFICATION_KEY_FILE , verification_key_byteblob );
   hexfile_of_byteblob( "verifkey.hex", verification_key_byteblob );
 
 }
 
-void use_circuit( std::string passphrase, std::string pubkey ){
+void use_circuit_old( std::string passphrase, std::string pubkey ){
 
   std::vector<uint32_t> passphrase32(4);
   std::vector<uint32_t> pubkey32(4);
@@ -323,7 +325,8 @@ void use_circuit( std::string passphrase, std::string pubkey ){
 
   snark::r1cs_variable_assignment<field_type> values = bp.full_variable_assignment();
 
-  values[ 0 ] = pubkey32[0];
+  // values[ 0 ] = pubkey32[0];
+  bp.val( public_pubkey0 ) = pubkey32[0];
[…]

### 2021-07-12 01_sudoku/cpp/sudoku.cpp
remove useless comment in sudoku.cpp

@@ -252,65 +252,6 @@ blueprint<curves::bls12<381>::scalar_field_type> build_blueprint(bool with_insta
     }
 
     // Add witness values
-/*    bp.val(x_0_0) = 1;
-    bp.val(x_0_1) = 2;
-    bp.val(x_0_2) = 3;
-    bp.val(x_0_3) = 4;
-
-    bp.val(x_1_0) = 3;
-    bp.val(x_1_1) = 4;
-    bp.val(x_1_2) = 2;
-    bp.val(x_1_3) = 1;
-
-    bp.val(x_2_0) = 2;
-    bp.val(x_2_1) = 1;
-    bp.val(x_2_2) = 4;
-    bp.val(x_2_3) = 3;
-
-    bp.val(x_3_0) = 4;
-    bp.val(x_3_1) = 3;
-    bp.val(x_3_2) = 1;
-    bp.val(x_3_3) = 2;*/
-
-    /*bp.val(free_x_0_0) = 0;
-    bp.val(free_x_0_1) = 0;
-    bp.val(free_x_0_2) = 0;
-    bp.val(free_x_0_3) = 0;
-
-    bp.val(free_x_1_0) = 0;
-    bp.val(free_x_1_1) = 0;
-    bp.val(free_x_1_2) = 0;
-    bp.val(free_x_1_3) = 0;
-
-    bp.val(free_x_2_0) = 0;
-    bp.val(free_x_2_1) = 0;
-    bp.val(free_x_2_2) = 0;
-    bp.val(free_x_2_3) = 0;
-
-    bp.val(free_x_3_0) = 0;
-    bp.val(free_x_3_1) = 0;
-    bp.val(free_x_3_2) = 0;
-    bp.val(free_x_3_3) = 0;*/
-
-/*    bp.val(free2_x_0_0) = 0;
-    bp.val(free2_x_0_1) = 0;
-    bp.val(free2_x_0_2) = 0;
-    bp.val(free2_x_0_3) = 0;
-
-    bp.val(free2_x_1_0) = 0;
-    bp.val(free2_x_1_1) = 0;
-    bp.val(free2_x_1_2) = 0;
-    bp.val(free2_x_1_3) = 0;
-
-    bp.val(free2_x_2_0) = 0;
-    bp.val(free2_x_2_1) = 0;
-    bp.val(free2_x_2_2) = 0;
-    bp.val(free2_x_2_3) = 0;
-
[…]

### 2021-07-12 bin/cli/src/circuit.hpp
refactor circuit

@@ -12,21 +12,25 @@ using namespace nil::crypto3::zk::components;
 //using namespace nil::crypto3::algebra;
 using namespace nil::crypto3::zk::snark;
 
-namespace circuit {
-    template <typename FieldType>
-    struct generated_primary_input {
-        typename FieldType::value_type signed_vote;
-        typename FieldType::value_type anonymous_id;
-    };
-}
 
-namespace {
+class circuit {
+public:
+    static const std::size_t SECRET_BITS_SIZE = 256;
+    static const std::size_t PRIMARY_INPUT_SIZE = 13;
+    static const std::size_t MAX_ENTRIES = 10;
+    static const std::size_t VOTE_MSG_LEN = 32;
+    static const std::size_t HASH_MSG_LEN = 33;
+    static const std::size_t ANONYMOUS_ID_MSG_LEN = 34;
+
+private:
     template <typename FieldType>
-    blueprint<FieldType> generate_circuit_internal(
+    static blueprint<FieldType> generate_circuit_internal(
         const std::vector<typename FieldType::value_type> &hashes_field_elements={},
         const std::vector<bool> &secret_bv={},
         std::uint32_t vote_choice=0,
-        circuit::generated_primary_input<FieldType> *primary_input_out = nullptr,
+        std::size_t secret_hash_index = 0,
+        const typename FieldType::value_type &vote_choice_hmac_value = 0,
+        const typename FieldType::value_type &anonymous_id_value = 0,
         bool generate_witness = false
         ) {
         typedef hmac_component<FieldType,
@@ -34,14 +38,8 @@ namespace {
                         knapsack_crh_with_field_out_component<FieldType>>
             Hmac;
 
-        const std::size_t SECRET_BITS_SIZE = 256;
         constexpr const std::size_t modulus_bits = FieldType::modulus_bits;
         constexpr const std::size_t modulus_chunks = modulus_bits / 8 + (modulus_bits % 8 ? 1 : 0);
-        const std::size_t PRIMARY_INPUT_SIZE = 13;
-        const std::size_t MAX_ENTRIES = 10;
-        const std::size_t VOTE_MSG_LEN = 32;
-        const std::size_t HASH_MSG_LEN = 33;
-        const std::size_t ANONYMOUS_ID_MSG_LEN = 34;
 
 
         blueprint<FieldType> bp;
@@ -139,7 +137,6 @@ namespace {
         if(generate_witness) {
[…]

### 2021-07-12 bin/cli/src/main.cpp

@@ -204,20 +204,46 @@ int main(int argc, char *argv[]) {
         for (size_t i = hashes_bytes.size(); i < hashes_field_elements.size(); ++i) {
             hashes_field_elements[i] = field_type::value_type::zero();
         }
-        circuit::generated_primary_input<field_type> primary_input;
+
+        field_type::value_type hash =
+            Hmac::get_hmac(secret_bv, std::vector<bool>(HASH_MSG_LEN, 1)) [0];
+        field_type::value_type anonymous_id =
+            Hmac::get_hmac(secret_bv, std::vector<bool>(ANONYMOUS_ID_MSG_LEN, 1)) [0];
+        
+        std::vector<bool> vote_choice_bv(VOTE_MSG_LEN);
+
+        for(std::size_t i = 0, temp = vote_choice; i < VOTE_MSG_LEN; ++i) {
+            vote_choice_bv[i] = temp&1;
+            temp >>= 1;
+        }
+
+        field_type::value_type vote_choice_hmac =
+            Hmac::get_hmac(secret_bv, vote_choice_bv) [0];
+
+        std::size_t index = 
+            std::find(hashes_field_elements.begin(),
+                      hashes_field_elements.end(),
+                      hash) - hashes_field_elements.begin();
+
+        if(index < 0 ) {
+            std::cout << "The voting secret's hash is not in the voters hashes list" << std::endl;
+            return 1;
+        }
+        
+
         bp = circuit::generate_circuit_with_witness<field_type>(
             hashes_field_elements,
             secret_bv,
             vote_choice,
-            &primary_input
+            index,
+            vote_choice_hmac,
+            anonymous_id
         );
         std::cout << "is blueprint satisfied:" << (bp.is_satisfied() ? "true" : "false") << std::endl;
 
-        std::string signed_vote_hex = field_element_to_hex(primary_input.signed_vote);
-        std::cout << "Your signed vote is: " << signed_vote_hex << std::endl;
+        std::cout << "Your signed vote is: " << field_element_to_hex(vote_choice_hmac) << std::endl;        
+        std::cout << "Your anonymous voter id is: " << field_element_to_hex(anonymous_id) << std::endl;
 
-        std::string anonymous_id_hex = field_element_to_hex(primary_input.anonymous_id);
-        std::cout << "Your anonymous voter id is: " << anonymous_id_hex << std::endl;
     }
     
     typename scheme_type::keypair_type keypair;

### 2021-07-12 bin/cli/src/main.cpp
do not dserialize verification key

@@ -246,13 +246,15 @@ int main(int argc, char *argv[]) {
 
     }
     
-    typename scheme_type::keypair_type keypair;
+    typename scheme_type::proving_key_type proving_key;
     if (vm.count("generate-keypair")) {
         std::cout << "Starting generator" << std::endl;
-        zk::snark::r1cs_constraint_system<field_type> constraint_system = bp.get_constraint_system();
+        zk::snark::r1cs_constraint_system<field_type> constraint_system =
+            bp.get_constraint_system();
         std::cout << constraint_system.num_constraints() << std::endl;
         std::cout << constraint_system.num_variables() << std::endl;
-        keypair = zk::snark::generate<scheme_type>(constraint_system);
+        typename scheme_type::keypair_type keypair =
+             zk::snark::generate<scheme_type>(constraint_system);
         std::vector<std::uint8_t> verification_key_byteblob =
             serializer_tvm::process(keypair.second);
         write_vector_to_disk(vkout, verification_key_byteblob);
@@ -260,30 +262,20 @@ int main(int argc, char *argv[]) {
         std::vector<std::uint8_t> proving_key_byteblob =
             serializer_tvm::process(keypair.first);
         write_vector_to_disk(pkout, proving_key_byteblob);
-    } else{
-        std::cout << "Loading keypair" << std::endl;
+
+        proving_key=keypair.first;
+    } else {
+        std::cout << "Loading proving key" << std::endl;
         std::vector<uint8_t> proving_key_byteblob = read_vector_from_disk(pkout);
         nil::marshalling::status_type pk_desrialize_status;
-        keypair.first =
+        proving_key =
              deserializer_tvm::proving_key_process(proving_key_byteblob.begin(),
                                                    proving_key_byteblob.end(),
                                                    pk_desrialize_status);
 
-        std::vector<uint8_t> verification_key_byteblob = read_vector_from_disk(vkout);
-        
         if(pk_desrialize_status != nil::marshalling::status_type::success) {
-            std::cerr << "Error: Could not deserialize proving key";
-            return 1;
-        }
-
-        nil::marshalling::status_type vk_desrialize_status;
-        keypair.second =
-            deserializer_tvm::verification_key_process(verification_key_byteblob.begin(),
-                                                  verification_key_byteblob.end(),
-                                                  vk_desrialize_status);
-
[…]

### 2021-07-13 03_pincode/cpp/build.sh
euler-client C++ program

@@ -1,43 +1,3 @@
 #!/bin/sh
 
-if [ -f picosha2.h ]; then
-    echo Error: you should rename picosha2.h to picosha2.hpp
-    echo Only sources with .hpp and .cpp are supported
-    exit 2
-fi
-
-
-CURDIR=$(pwd)
-FILES=$(ls *.hpp *.cpp)
-touch $FILES
-
-ROOTDIR=$(cd ../..; pwd)
-
-cd $ROOTDIR
-if [ ! -f ton-proof-verification-contest/CMakeLists.txt ]; then
-    git clone --recursive https://github.com/NilFoundation/ton-proof-verification-contest.git
-fi
-
-cd ton-proof-verification-contest
-if [ ! -f build/Makefile ]; then
-  mkdir build
-  cd build
-  cmake ..
-  cd ..
-fi
-
-rm -f bin/cli/src/*.cpp
-rm -f bin/cli/src/*.hpp
-
-for file in $FILES; do
-    ln -sf $CURDIR/$file bin/cli/src/$file
-done
-
-cd build
-make cli || exit 2
-
-cp -f bin/cli/cli $CURDIR/pincode-client
-
-
-
-
+../../common/build.sh pincode-client

### 2021-07-13 common/build.sh

@@ -1,0 +1,52 @@
+#!/bin/sh
+
+if [ "X$1" = "X" ] ; then
+    echo "Usage: ./build.sh COMMAND"
+    echo "  COMMAND is the name of the executable to create in the current dir"
+    exit 2
+fi
+
+COMMAND=$1
+
+cp -f ../../include/*.hpp .
+
+if [ -f picosha2.h ]; then
+    echo Error: you should rename picosha2.h to picosha2.hpp
+    echo Only sources with .hpp and .cpp are supported
+    exit 2
+fi
+
+CURDIR=$(pwd)
+FILES=$(ls *.hpp *.cpp)
+touch $FILES
+
+ROOTDIR=$(cd ../..; pwd)
+
+cd $ROOTDIR
+if [ ! -f ton-proof-verification-contest/CMakeLists.txt ]; then
+    git clone --recursive https://github.com/NilFoundation/ton-proof-verification-contest.git
+fi
+
+cd ton-proof-verification-contest
+if [ ! -f build/Makefile ]; then
+  mkdir build
+  cd build
+  cmake ..
+  cd ..
+fi
+
+rm -f bin/cli/src/*.cpp
+rm -f bin/cli/src/*.hpp
+
+for file in $FILES; do
+    ln -sf $CURDIR/$file bin/cli/src/$file
+done
+
+cd build
+make cli || exit 2
+
+cp -f bin/cli/cli $CURDIR/$COMMAND
+
+
+
+

### 2021-07-13 include/utils.hpp

@@ -1,0 +1,195 @@
+
+#include <sys/stat.h>
+
+inline bool file_exists (const std::string& name) {
+  struct stat buffer;   
+  return (stat (name.c_str(), &buffer) == 0); 
+}
+
+template <typename InIter>
+void output_hex(InIter first, InIter last, std::ostream& os) {
+    os.setf(std::ios::hex, std::ios::basefield);
+    while (first != last) {
+        os.width(2);
+        os.fill('0');
+        os << static_cast<unsigned int>(*first);
+        ++first;
+    }
+    os.setf(std::ios::dec, std::ios::basefield);
+}
+
+template <typename InIter>
+void bytes_to_hex_string(InIter first, InIter last, std::string& hex_str) {
+    std::ostringstream oss;
+    output_hex(first, last, oss);
+    hex_str.assign(oss.str());
+}
+
+template <typename InContainer>
+void bytes_to_hex_string(const InContainer& bytes, std::string& hex_str) {
+    bytes_to_hex_string(bytes.begin(), bytes.end(), hex_str);
+}
+
+template <typename InIter>
+std::string bytes_to_hex_string(InIter first, InIter last) {
+    std::string hex_str;
+    bytes_to_hex_string(first, last, hex_str);
+    return hex_str;
+}
+
+template <typename InContainer>
+std::string bytes_to_hex_string(const InContainer& bytes) {
+    std::string hex_str;
+    bytes_to_hex_string(bytes, hex_str);
+    return hex_str;
+}
+
+std::vector<uint8_t> read_vector_from_disk(std::string file)
+{  
+  cerr << "Loading from '" << file << "." << endl ;
+  if( ! file_exists(file) ){
+    cerr << "Error: file does not exist" << endl ;
+    exit(2) ;
+  }
+  
+  std::ifstream instream(file, std::ios::in | std::ios::binary);
+  std::vector<uint8_t> data((std::istreambuf_iterator<char>(instream)), std::istreambuf_iterator<char>());
+  return data;
+}
+
+
+void append_to_byteblob( std::vector<std::uint8_t> &byteblob, std::vector<std::uint8_t> bytes)
+{
+  byteblob.insert (byteblob.end(), bytes.begin(), bytes.end());
+}
+
+void hexfile_of_byteblob( std::string file,  std::vector<std::uint8_t> byteblob ){
+  std::string hex_str = bytes_to_hex_string(byteblob.begin(), byteblob.end());
[…]

### 2021-07-13 common/build.sh
start Euler contracts

@@ -8,7 +8,7 @@ fi
 
 COMMAND=$1
 
-cp -f ../../include/*.hpp .
+cp -f ../../common/*.hpp .
 
 if [ -f picosha2.h ]; then
     echo Error: you should rename picosha2.h to picosha2.hpp

### 2021-07-13 02_euler/tests/00_init.sh
working Euler

@@ -1,0 +1,18 @@
+#!/bin/bash
+
+. ./env.sh
+
+$FT switch to testnet
+$FT --switch sandbox1 node stop
+$FT switch remove sandbox1
+
+$FT switch create sandbox1 --image ocamlpro/nil-local-node || exit 2
+
+$FT node start || exit 2
+
+echo Node is starting... waiting 10 seconds
+sleep 10
+
+$FT node give user0 user1 user2 --amount 100000 || exit 2
+
+

### 2021-07-13 02_euler/tests/01_prepare.sh

@@ -1,0 +1,5 @@
+#!/bin/bash
+
+. ./env.sh
+
+$FT exec -- ../cpp/euler-client prepare ${EULER_PROBLEM} ${EULER_SOLUTION} || exit 2

### 2021-07-13 02_euler/tests/02_deploy.sh

@@ -1,0 +1,12 @@
+#!/bin/bash
+
+. ./env.sh
+
+$FT contract deploy EulerRoot --deployer user0 --credit 100 '{ "problem_code": "%{get-code:contract:tvc:EulerProblem}", "user_code": "%{get-code:contract:tvc:EulerUser}" }' -f || exit 2
+
+$FT call --local EulerRoot get || exit 2
+
+
+
+
+

### 2021-07-13 02_euler/tests/03_new_problem.sh

@@ -1,0 +1,19 @@
+#!/bin/bash
+
+. ./env.sh
+
+$FT call EulerRoot new_problem '{ "problem": %{env:EULER_PROBLEM}, "verifkey": "%{file:verifkey.bin.hex}", "zip_provkey": "%{hex:file:provkey.bin.zip}" }' --wait || exit 2
+
+zip provkey.bin.zip provkey.bin || exit 2
+
+rm -f euler_problem.addr
+$FT call --local EulerRoot problem_address '{ "problem": %{env:EULER_PROBLEM} }' --subst @%{res:addr} --output euler_problem.addr || exit 2
+
+$FT account create euler_problem --address "$(cat euler_problem.addr)" --contract EulerProblem || exit 2
+
+$FT call --local euler_problem get || exit 2
+
+
+
+
+

### 2021-07-13 02_euler/tests/04_new_user.sh

@@ -1,0 +1,20 @@
+#!/bin/bash
+
+. ./env.sh
+
+$FT multisig transfer 1 --from user1 --to EulerRoot new_user '{ "pubkey": "0x%{account:pubkey:user1}" }' --wait || exit 2
+
+rm -f user.addr
+$FT call --local EulerRoot user_address '{ "pubkey": "0x%{account:pubkey:user1}" }' --subst @%{res:addr} --output user.addr || exit 2
+
+$FT account create euler_user --address "$(cat user.addr)" --contract EulerUser || exit 2
+
+$FT call --sign user1 euler_user set_name '{ "name": "%{hex:string:John Doo}" }' || exit 2
+
+$FT call --local euler_user get || exit 2
+
+
+
+
+
+

### 2021-07-13 02_euler/tests/05_submit.sh

@@ -1,0 +1,19 @@
+#!/bin/bash
+
+. ./env.sh
+
+
+$FT exec -- ../cpp/euler-client prove ${EULER_PROBLEM} ${EULER_SOLUTION} '%{account:pubkey:user1}' || exit 2
+
+
+
+$FT multisig transfer 1 --from user1 --to EulerRoot submit '{ "problem": %{env:EULER_PROBLEM}, "proof": "%{file:proof.bin.hex}", "pubkey": "0x%{account:pubkey:user1}" }' --wait || exit 2
+
+
+
+
+
+
+
+
+

### 2021-07-13 02_euler/tests/06_submit.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+
+. ./env.sh
+
+
+$FT exec -- ../cpp/euler-client prove ${EULER_PROBLEM} ${EULER_SOLUTION} '%{account:pubkey:user2}' || exit 2
+
+
+
+$FT multisig transfer 1 --from user2 --to EulerRoot submit '{ "problem": %{env:EULER_PROBLEM}, "proof": "%{file:proof.bin.hex}", "pubkey": "0x%{account:pubkey:user2}" }' --wait || exit 2
+
+
+$FT call --local euler_problem get    

### 2021-07-13 02_euler/tests/env.sh

@@ -1,0 +1,23 @@
+
+function cmd()
+{
+    echo
+    echo  COMMAND $*
+    echo
+    $* || exit 2
+}
+
+function cmdk()
+{
+    echo
+    echo  COMMAND $*
+    echo
+    $*
+}
+
+FT="ft --echo"
+
+
+export EULER_PROBLEM=101
+export EULER_SOLUTION=777
+

### 2021-07-13 02_euler/cpp/main.cpp
Improve Euler contracts and tests

@@ -83,46 +83,8 @@ using field_type = typename curve_type::scalar_field_type;
 #include "utils.hpp"
 
 
-// This function translates a bytes[32] vector into a uint32[4]
-// vector, by keeping only the first 16 bytes, and removing one bit to
-// remain positive.  The result is only 124 bits long, but it's enough
-// to keep finding collisions computationnaly impossible.
-void uint32s_of_bytes( std::vector<uint32_t> &uints, std::vector<uint8_t> &bytes )
-{
-  for( int i = 0 ; i<4; i++ ){
-    uints[i] =
-      ( (uint32_t) bytes[ 4*i] ) +
-      ( ( (uint32_t) bytes[ 4*i+1 ] ) << 8 ) +
-      ( ( (uint32_t) bytes[ 4*i+2 ] ) << 16 ) +
-      ( ( (uint32_t) bytes[ 4*i+3 ] & 0x7f ) << 24 ) ;
-  }
-}
-
-
-void uint32s_of_passphrase( std::vector<uint32_t> &uints, std::string passphrase ){
-
-  std::vector<uint8_t> hash(picosha2::k_digest_size);
-
-  picosha2::hash256( passphrase.begin(), passphrase.end(), hash.begin(), hash.end());
-  uint32s_of_bytes( uints, hash );
-}
-
-void uint32s_of_pubkey( std::vector<uint32_t> &uints, std::string pubkey_s ){
-
-  std::vector<uint8_t> pubkey(32);
-
-  for( int i = 0 ; i < 32 ; i++ ){
-    pubkey[ i ] = int_of_hexchar( pubkey_s[ i*2 ] ) * 16 + int_of_hexchar( pubkey_s[ i*2+1 ] ) ;
-    // cerr << pubkey [ i ] << endl ;
-  }
-  uint32s_of_bytes( uints, pubkey );
-}
-
-
-
 void build_circuit ( blueprint<field_type> &bp,
-                     uint32_t problem_i32,
-                     uint32_t solution_i32 ){
+                     std::vector<uint32_t> &passphrase32 ){
 
   blueprint_variable<field_type> public_pubkey0;
   public_pubkey0.allocate( bp );
@@ -148,42 +110,69 @@ void build_circuit ( blueprint<field_type> &bp,
   blueprint_variable<field_type> secret_pubkey3;
   secret_pubkey3.allocate( bp );
 
-  blueprint_variable<field_type> secret_problem;
-  secret_problem.allocate( bp );
[…]

### 2021-07-13 02_euler/tests/00_init_sandbox.sh

@@ -13,6 +13,6 @@ $FT node start || exit 2
 echo Node is starting... waiting 10 seconds
 sleep 10
 
-$FT node give user0 user1 user2 --amount 100000 || exit 2
+$FT node give user0 user1 user2 user3 --amount 100000 || exit 2
 
 

### 2021-07-13 02_euler/tests/00_init_testnet.sh

@@ -1,0 +1,14 @@
+#!/bin/bash
+
+. ./env.sh
+
+# To run this script, you need to have already configured a switch 'nil'
+# containing Surf accounts user0..user3. Use './create_nil_accounts.sh'
+# to create these accounts
+
+$FT switch to testnet || exit 2
+$FT switch remove nil_euler
+$FT switch create nil_euler --url https://net.freeton.nil.foundation/ || exit 2
+$FT account copy from nil user0 user1 user2 user3 || exit 2
+
+

### 2021-07-13 02_euler/tests/01_prepare.sh

@@ -2,4 +2,6 @@
 
 . ./env.sh
 
-$FT exec -- ../cpp/euler-client prepare ${EULER_PROBLEM} ${EULER_SOLUTION} || exit 2
+$FT exec -- ../cpp/euler-client prepare ${EULER_PROBLEM} ${EULER_NONCE} ${EULER_SOLUTION} || exit 2
+
+zip provkey.bin.zip provkey.bin || exit 2

### 2021-07-13 02_euler/tests/02_deploy.sh

@@ -2,7 +2,9 @@
 
 . ./env.sh
 
-$FT contract deploy EulerRoot --deployer user0 --credit 100 '{ "problem_code": "%{get-code:contract:tvc:EulerProblem}", "user_code": "%{get-code:contract:tvc:EulerUser}" }' -f || exit 2
+$FT contract deploy EulerRoot --deployer user0 --credit 2 '{ "problem_code": "%{get-code:contract:tvc:EulerProblem}", "user_code": "%{get-code:contract:tvc:EulerUser}" }' -f || exit 2
+
+$FT account info EulerRoot
 
 $FT call --local EulerRoot get || exit 2
 

### 2021-07-13 02_euler/tests/03_new_problem.sh

@@ -2,9 +2,9 @@
 
 . ./env.sh
 
-$FT call EulerRoot new_problem '{ "problem": %{env:EULER_PROBLEM}, "verifkey": "%{file:verifkey.bin.hex}", "zip_provkey": "%{hex:file:provkey.bin.zip}" }' --wait || exit 2
+$FT call EulerRoot new_problem '{ "problem": %{env:EULER_PROBLEM}, "verifkey": "%{file:verifkey.bin.hex}", "zip_provkey": "%{hex:file:provkey.bin.zip}", "nonce": "%{env:EULER_NONCE}", "title": "%{hex:string:Example}", "description": "%{hex:string:a very basic example}", "url": "%{hex:string:https://euler.org/}" }' --wait || exit 2
 
-zip provkey.bin.zip provkey.bin || exit 2
+$FT account info EulerRoot
 
 rm -f euler_problem.addr
 $FT call --local EulerRoot problem_address '{ "problem": %{env:EULER_PROBLEM} }' --subst @%{res:addr} --output euler_problem.addr || exit 2

### 2021-07-13 02_euler/tests/05_submit_user1.sh

@@ -3,17 +3,11 @@
 . ./env.sh
 
 
-$FT exec -- ../cpp/euler-client prove ${EULER_PROBLEM} ${EULER_SOLUTION} '%{account:pubkey:user1}' || exit 2
+$FT exec -- ../cpp/euler-client prove ${EULER_PROBLEM} ${EULER_NONCE} ${EULER_SOLUTION} '%{account:pubkey:user1}' || exit 2
 
 
 
 $FT multisig transfer 1 --from user1 --to EulerRoot submit '{ "problem": %{env:EULER_PROBLEM}, "proof": "%{file:proof.bin.hex}", "pubkey": "0x%{account:pubkey:user1}" }' --wait || exit 2
 
-
-
-
-
-
-
-
-
+$FT call --local euler_user get    
+$FT call --local euler_problem get    

### 2021-07-13 02_euler/tests/06_submit_user2.sh

@@ -3,7 +3,7 @@
 . ./env.sh
 
 
-$FT exec -- ../cpp/euler-client prove ${EULER_PROBLEM} ${EULER_SOLUTION} '%{account:pubkey:user2}' || exit 2
+$FT exec -- ../cpp/euler-client prove ${EULER_PROBLEM} ${EULER_NONCE}  ${EULER_SOLUTION} '%{account:pubkey:user2}' || exit 2
 
 
 

### 2021-07-13 02_euler/tests/07_submit_user3.sh

@@ -1,0 +1,14 @@
+#!/bin/bash
+
+. ./env.sh
+
+
+$FT multisig transfer 1 --from user3 --to EulerRoot submit '{ "problem": %{env:EULER_PROBLEM}, "proof": "%{file:proof.bin.hex}", "pubkey": "0x%{account:pubkey:user3}" }' --wait || exit 2
+
+$FT call --local euler_problem get
+
+# wrong solution:
+
+$FT exec -- ../cpp/euler-client prove ${EULER_PROBLEM} ${EULER_NONCE}  ${EULER_SOLUTION}0 '%{account:pubkey:user3}' && echo OK
+
+$FT call --local euler_problem get    

### 2021-07-13 02_euler/tests/env.sh

@@ -19,5 +19,6 @@ FT="ft --echo"
 
 
 export EULER_PROBLEM=101
+export EULER_NONCE=478478
 export EULER_SOLUTION=777
 

### 2021-07-13 03_pincode/cpp/main.cpp

@@ -83,42 +83,6 @@ using field_type = typename curve_type::scalar_field_type;
 #include "utils.hpp"
 
 
-// This function translates a bytes[32] vector into a uint32[4]
-// vector, by keeping only the first 16 bytes, and removing one bit to
-// remain positive.  The result is only 124 bits long, but it's enough
-// to keep finding collisions computationnaly impossible.
-void uint32s_of_bytes( std::vector<uint32_t> &uints, std::vector<uint8_t> &bytes )
-{
-  for( int i = 0 ; i<4; i++ ){
-    uints[i] =
-      ( (uint32_t) bytes[ 4*i] ) +
-      ( ( (uint32_t) bytes[ 4*i+1 ] ) << 8 ) +
-      ( ( (uint32_t) bytes[ 4*i+2 ] ) << 16 ) +
-      ( ( (uint32_t) bytes[ 4*i+3 ] & 0x7f ) << 24 ) ;
-  }
-}
-
-
-void uint32s_of_passphrase( std::vector<uint32_t> &uints, std::string passphrase ){
-
-  std::vector<uint8_t> hash(picosha2::k_digest_size);
-
-  picosha2::hash256( passphrase.begin(), passphrase.end(), hash.begin(), hash.end());
-  uint32s_of_bytes( uints, hash );
-}
-
-void uint32s_of_pubkey( std::vector<uint32_t> &uints, std::string pubkey_s ){
-
-  std::vector<uint8_t> pubkey(32);
-
-  for( int i = 0 ; i < 32 ; i++ ){
-    pubkey[ i ] = int_of_hexchar( pubkey_s[ i*2 ] ) * 16 + int_of_hexchar( pubkey_s[ i*2+1 ] ) ;
-    // cerr << pubkey [ i ] << endl ;
-  }
-  uint32s_of_bytes( uints, pubkey );
-}
-
-
 
 void build_circuit ( blueprint<field_type> &bp, std::vector<uint32_t> &passphrase32 ){
 

### 2021-07-13 submission/submission.tex
improve sudoku section, intro + images

@@
 \usepackage{amssymb}
+\usepackage{mathtools}
 \usepackage{graphicx}
@@
 
+\input{solidity-highlighting}
+
 \lstdefinestyle{BashInputStyle}{
@@
 
-\author{OcamlPro - Fabrice Le Fessant et Thomas Sibut-Pinote}
-\title{Groth16 zkSNARK Proof Verification on Freeton : Three Use Cases}
+\author{OcamlPro - Fabrice Le Fessant\footnote{Telegram: @fabrice\_dune} and Thomas Sibut-Pinote\footnote{Telegram: @ThomasSibutPinote}}
+\title{Groth16 zk-SNARK Proof Verification on Freeton : Three Use Cases}
 
@@
 
+\newcommand{\zksnark}{zk-SNARK}
+\newcommand{\zksnarks}{zk-SNARKs}
+
+\section{Introduction}
+\label{sec:intro}
+
+\subsection{Description of the submission}
+\label{subsec:description}
+
 The present document is an official submission to the 18$^{\text{th}}$
 contest\footnote{\url{https://devex.gov.freeton.org/proposal?proposalAddress=0\%3Ae6b65075478e7d412fdb0870452f30dfa8bf51272e28a3167abc5c5df6fd051d}}
-of the DevEx governance: {\em Groth16 zkSNARK Proof Verification Use
+of the DevEx governance: {\em Groth16 \zksnark{} Proof Verification Use
   Cases}. Although we accepted earlier to be part of the jury, we
@@
 In this submission, we propose three different use cases for Groth16
-zkSNARK proofs on the FreeTON blockchain:
+\zksnark{} proofs on the FreeTON blockchain:
 \begin{itemize}
-\item Sudoky: Zksnarks are used to prove that the user has a solution
-  to a given Sudoky problem, without providing the solutions to other
+\item (Section~\ref{section_sudoku}) Sudoku: \zksnarks{} are used to prove that the user has a solution
+  to a given Sudoku problem, without providing the solutions to other
   users ;
-\item Euler Project: Zksnarks are used to prove that the user has
-  found the solution to an Euler problem ;
-\item Pin-code reset of forgotten keys: Zksnarks are used to replace a
-  pubkey when the user has lost his secret key
+\item (Section~\ref{section_euler})Project Euler: \zksnarks{} are used to prove that the user has found the solution to a math problem from the famous \url{https://projecteuler.net} website;
+\item (Section~\ref{section_pincode})Pin-code reset of forgotten keys: \zksnarks{} are used to replace a
+  pubkey when the user has lost his secret key.
 \end{itemize}
 
-Finally, we finish this document by a section showing the
-contributions that we did for the Free TON community while working on
-this contest.
+We then show the contributions that we made for the Free TON community while working on
+this contest (Section~\ref{sec:contributions}). Finally, we discuss the three paradigms of using \zksnarks{} that our examples showcase.
+
+\subsection{General remarks}
+\label{subsec:general_remarks}
+
+\begin{description}
+	\item[Code:] All our code comes with a README and tests.
+This document is provided as an overview of our use cases for \zksnarks{} on the Freeton blockchain but you can also directly plunge into the code.
+All our code is under the GPL license and is hosted at \url{https://github.com/OCamlPro/devex-18-zk-contest}.
+
+	\item[Compilation time:] The long compilation time of the repository provided was a major obstacle in our progression. We would suggest trying to make it shorter for future contests.
+
+	\item[Marshalling and memory corruption:] Because of a memory corruption error in the marshalling of the verification key, we were unable to do a full 9 by 9 Sudoku, restricting ourselves to 4 by 4.
+All our code is generic (it is generated from an Ocaml program which takes as a parameter the value $n$ such that the Sudoku is $n^2$ by $n^2$).
+We were told that after the contest, a more robust marshalling library would be provided.
+In any case we would be glad to discuss this issue with the Nil foundation team to give users the full Sudoku experience!
+In the meantime, a 4 by 4 Sudoku is sufficient to get a sense of the dynamics of \zksnark-based Sudoku.
+
+	\item[Keys on contracts: ] For all of our smart contracts, we provided, along with the verification key as needed by the \verb|vergroth16| instruction, the proving key (in a zipped) on the smart contract.
+This enables users to easily find it in order to generate their proofs.
+In case the contract deployer should decide to keep the possibility of changing the verification and proving keys of the problem(s), this also makes it easiest to follow changes before submitting a solution.
+
+	\item[Thanks:] We would like to thank @noam for his efforts and sportsmanship during the contest, and to the Nil foundation team for their answers to our various questions.
+\end{description}
 
@@
 \label{section_sudoku}
+
+	\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.6\textwidth]{Sudoku04}
+	\caption{A Sudoku grid}
+	\end{figure}
 
@@
 All the other students can cheat by copying it, instead of doing the work by themselves, which defeats the whole purpose.
-One other advantage is that we don't need to implement the whole logic of the computation on the smart contract.
-For some size of Sudoku, this is probably worthwhile.
+
+As mentioned in Section \ref{subsec:general_remarks}, we had to restrict ourselves to a 4 by 4 Sudoku grid, even though our code generator is generic in the grid size.
+This is because the marshalling function on the 9 by 9 code produced a memory corruption error.
+
+\subsection{Mathematical encoding}
+\label{subsec:math_enc}
+
+Let $n^2$ be the size of a Sudoku grid (in our case, $n=2$ and $n^2 = 4$ is the length of a side of the Sudoku square).In the following, the variables $(x_{i,j})_{0 \leq i,j < n^2}$ denote the (secret) values of the solution of a given instance of a Sudoku.
+The variables $(f_{i,j})_{0 \leq i,j < n^2}$ denote the instance so that
+\begin{equation}
+f_{i,j} =
+\begin{cases*}
+0 & if \textrm{square $i$,$j$ is not fixed by the Sudoku instance}\\
+\textrm{The value in square $i$,$j$ }        & otherwise
+\end{cases*}
+\end{equation}
+The (well-known) constraints of a Sudoku are encoded by the following equations:
+\[ \prod_{k=1}^{n^2} \left( x_{i,j} - k \right) = 0 \textrm{ for all $0 \leq i,j < n^2$} \]
+and
+\[ f_{i,j} x_{i,j} = f_{i,j}^2 \textrm{ for all $0 \leq i,j < n^2$}\]
+and, for all $S$ set of indices representing a row, a column or a box as per the rules of Sudoku:
+\[ \prod_{(i,j) \in S} x_{i,j} = \prod_{k=1}^{n^2} k = \left(n^2\right)! \; .\]
+
+The first equations guarantee that the only permitted values for $x_{i,j}$ are the integers from $1$ through $n^2$, while the second force
+
+\[ \forall 0 \leq i,j < n^2, f_{i,j} \neq 0 \implies x_{i,j} = f_{i,j}.\]
+
+The last equation, by forcing the product of $n^2$ integers between 1 and $n^2$ to be equal to $\left(n^2\right)!$, forces every row, column and box to contain one and only one instance of the integers $1$ through $9$.
+
+%One other advantage is that we don't need to implement the whole logic of the computation on the smart contract. For some size of Sudoku, this is probably worthwhile.
+
+\subsection{Components}
+\label{subsec:components}
+
+This use case includes two different components:
+
+\begin{description}
+	\item[The cli:] it is a C++ program linked to the Blueprint \zksnarks{} library. It can be used in two different ways:
+	\begin{itemize}
+		\item To create the original proving and verification keys. This step is independent of any given Sudoku instance and should only be done once.
+		\item To generate a proof given an instance and a solution. The instance is given as a text file such as
+
+		\begin{verbatim}
+			0000
+			0000
+			0000
+			0001
+		\end{verbatim}
+
+		where $0$s denote free values. The solution should be a similar text files with no zeroes, such as
+
+		\begin{verbatim}
+			1234
+			3412
+			2143
+			4321
+		\end{verbatim}
+
+		Note that if your solution is not correct, this step will fail.
+	\end{itemize}
+    \item[The Sudoku smart contract:] The main function of this smart contract is
+    \begin{lstlisting}[language=Solidity]
+    function submit(bytes proof)
+        public view returns (bool res, string blob_str)
+    \end{lstlisting}
+    It will check the input proof against the verification key \lstinline[language=Solidity]|v_key| and the current instance \lstinline[language=Solidity]|m_instance|, both local to the contract.
+This instance is stored as an array of \lstinline[language=Solidity]|fixed_value|:
+    \begin{lstlisting}[language=Solidity]
+    struct fixed_value {
+      uint8 i;
+      uint8 j;
+      uint8 value;
+    }
+
+    \end{lstlisting}
+\end{description}
 
@@
 
-The previous example is somewhat limited by the fact that sudokus are easily solvable problems, either by hand or with a computer; they are not a realistic use case of zk-snarks.
+	\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{euler}
+	\caption{The first Project Euler problem}
+\end{figure}
+
+The previous example is somewhat limited by the fact that Sudokus are easily solvable problems, either by hand or with a computer; they are not a realistic use case of \zksnarks{}\footnote{Although they hint at a possible use for \zksnarks{}: checking a result without implementing its full logic in Solidity may save precious storage and computations on the blockchain}.
+
 Let's keep the idea of a decentralized classroom.
@@
 
+1 million SHA256 hashes (about 20 seconds on our machine) computed with input \verb|problem_number \| solution | nonce| \footnote{Where `|` denotes the concatenation of strings} to emulate the captchas on the Project Euler website.
+
 \section{Pin code reset for forgotten keys}
@@
 
-In this use case, we use Zksnarks to allow users to replace their
+In this use case, we use \zksnarks{} to allow users to replace their
 public keys in multisig wallets. The typical use is when a user has
@@
 contract, where a passphrase is associated to his public key. If he
-needs to change his public key, he can use Zksnarks to associate a new
+needs to change his public key, he can use \zksnarks{} to associate a new
 public key in his recovery contract, and tell multisig wallets to
@@
 \item[PinCode Client:] it is a C++ program linked to the Blueprint
-  Zksnarks library. It can be used in two different ways:
+  \zksnarks{} library. It can be used in two different ways:
   \begin{itemize}
@@
 \section{Contributions to the Free TON community}
+\label{sec:contributions}
 
@@
 Our first contribution is a public Docker image containing the TONOS
-SE compiled with Zksnarks support. The image is published as {\tt
+SE compiled with \zksnarks{} support. The image is published as {\tt
   ocamlpro/nil-local-node} and is built from
@@
 
-As a consequence, a Zksnark-ready sandbox (local network) can be
+As a consequence, a \zksnark-ready sandbox (local network) can be
 installed by simply running:
@@
 
+\section{Thoughts on three paradigms of \zksnarks{} on blockchains}
+\label{sec_three_paradigms}
+This contest has given us the opportunity to think harder about the types of use-cases of \zksnarks{} on blockchains.
+
 \end{document}

### 2021-07-13 contracts/deploy_debot.sh
Init

@@ -1,0 +1,75 @@
+
+#!/bin/bash
+set -xe
+
+tos=tonos-cli
+
+DEBOT_NAME=SubsMan
+DEBOT_CLIENT=deployerDebot
+giver=0:841288ed3b55d9cdafa806807f02a0ae0c169aa5edfe88a789a6482429756a94
+function giver {
+$tos --url $NETWORK call --abi ../local_giver.abi.json $giver sendGrams "{\"dest\":\"$1\",\"amount\":20000000000}"
+}
+function get_address {
+echo $(cat log.log | grep "Raw address:" | cut -d ' ' -f 3)
+}
+function genaddr {
+$tos genaddr $1.tvc $1.abi.json --genkey $1.keys.json > log.log
+}
+function deploy {
+echo GENADDR $1 ----------------------------------------------
+genaddr $1
+DEBOT_ADDRESS=$(get_address)
+echo GIVER $1 ------------------------------------------------
+giver $DEBOT_ADDRESS
+echo DEPLOY $1 -----------------------------------------------
+$tos --url $NETWORK deploy $1.tvc "{}" --sign $1.keys.json --abi $1.abi.json
+DEBOT_ABI=$(cat $1.abi.json | xxd -ps -c 20000)
+$tos --url $NETWORK call $DEBOT_ADDRESS setABI "{\"dabi\":\"$DEBOT_ABI\"}" --sign $1.keys.json --abi $1.abi.json
+echo -n $DEBOT_ADDRESS > $1.addr
+}
+
+function deployMsig {
+msig=SafeMultisigWallet
+echo GENADDR $msig ----------------------------------------------
+genaddr $msig
+ADDRESS=$(get_address)
+echo GIVER $msig ------------------------------------------------
+giver $ADDRESS
+echo DEPLOY $msig -----------------------------------------------
+PUBLIC_KEY=$(cat $msig.keys.json | jq .public)
+$tos --url $NETWORK deploy $msig.tvc "{\"owners\":[\"0x${PUBLIC_KEY:1:64}\"],\"reqConfirms\":1}" --sign $msig.keys.json --abi $msig.abi.json
+echo -n $ADDRESS > msig.addr
+mv $msig.keys.json msig.key
+}
+
[…]

### 2021-07-13 ts4.py

@@ -1,0 +1,11 @@
+import tonos_ts4.ts4 as ts4
+
+eq = ts4.eq
+ts4.init('c:/Users/renat/Subscriptions/contracts', verbose = False)
+# Load a contract from .tvc-file and deploy it into a virtual blockchain.
+# Constructor is called automatically.
+# After deployment, "logstr: Constructor" will appear in the output to facilitate the debugging process.
+subs = ts4.BaseContract('c:/Users/renat/Subscriptions/contracts/Subscription', ctor_params = {'wallet': '0:109474cf57d7551a8e491956e48e49f4984b32e5bfe19b57b4cc56c1234168c0'})
+print(subs.addr)
+answer = subs.call_getter('mywallet')
+print(ts4.cyan(answer))

### 2021-07-13 submission/submission.tex
various additions to submission, including philosophical conclusion

@@
 
-\author{OcamlPro - Fabrice Le Fessant\footnote{Telegram: @fabrice\_dune} and Thomas Sibut-Pinote\footnote{Telegram: @ThomasSibutPinote}}
+\author{OCamlPro - Fabrice Le Fessant\footnote{Telegram: @fabrice\_dune} and Thomas Sibut-Pinote\footnote{Telegram: @ThomasSibutPinote}}
 \title{Groth16 zk-SNARK Proof Verification on Freeton : Three Use Cases}
@@
 We then show the contributions that we made for the Free TON community while working on
-this contest (Section~\ref{sec:contributions}). Finally, we discuss the three paradigms of using \zksnarks{} that our examples showcase.
+this contest (Section~\ref{sec:contributions}). Finally, we discuss the three paradigms of using \zksnarks{} that our examples showcase (Section~\ref{sec_three_paradigms}).
 
@@
 	\item[Marshalling and memory corruption:] Because of a memory corruption error in the marshalling of the verification key, we were unable to do a full 9 by 9 Sudoku, restricting ourselves to 4 by 4.
-All our code is generic (it is generated from an Ocaml program which takes as a parameter the value $n$ such that the Sudoku is $n^2$ by $n^2$).
+All our code is generic (it is generated from an OCaml program which takes as a parameter the value $n$ such that the Sudoku is $n^2$ by $n^2$).
 We were told that after the contest, a more robust marshalling library would be provided.
@@
 In case the contract deployer should decide to keep the possibility of changing the verification and proving keys of the problem(s), this also makes it easiest to follow changes before submitting a solution.
+
+    \item[Separate submissions:] After deliberation, we decided to submit only one document rather than three separate submissions, in a spirit of coherence.
+We leave it to the appreciation of the jury whether this work deserves to be counted as several submissions.
 
@@
 
-\section{A better example: Project Euler}
+\section{Project Euler}
 \label{section_euler}
@@
 Can we make Project Euler decentralized?
-Using the idea from Section \ref{section_sudoku}, we can prevent users from stealing others' solutions \textbf{and} from brute-forcing them, due to the cost of generating proofs.
+Using \zksnarks{}, we can prevent users from stealing others' solutions \textbf{and} from brute-forcing them, due to the cost of generating proofs.
 
-1 million SHA256 hashes (about 20 seconds on our machine) computed with input \verb|problem_number \| solution | nonce| \footnote{Where `|` denotes the concatenation of strings} to emulate the captchas on the Project Euler website.
+The authentic first 50 problems from the Project Euler website\footnote{Solved by yours truly.}, are deployed and available on the Nil Foundation instance of the FreeTON blockchain.
+
+\subsection{Brute-force protection}
+\label{subsec:brute-force}
+
+Project Euler is sort of a gentlemen's competition.
+For example, competitors are supposed to have found the answer using a program running at most in one minute, but no mechanism enforces this.
+Still, some protections are in place, partly to enforce the spirit of the competition, and partly because of past abuse.
+For instance, a captcha system prevents one from attempting many solutions in a row.
+We decided to emulate the latter mechanism.
+If we simply gave a proving key to try and find the actual solution to the problem, users might be tempted to try to build a proof using every single integer until it works\footnote{We have noticed that although generating a correct proof may take time, an incorrect input is usually rejected in less than one second.}.
+Hence, the value they must find is actually
+\[ \textrm{SHA256}^{1\,000\,000}\left(problem\_number | solution | nonce\right)\]
+where the exponent denotes repeated application of the $\textrm{SHA256}$ hashing function, and `|` denotes the concatenation of strings.
+Note that this does not protect against replay attacks, which is why we also included a form of authentication described in Section~\ref{section_pincode}.
+This repeated application takes about 20 seconds on our laptops, which seems enough to discourage brute-force by all but the most determined cheaters.
+
+\subsection{Components}
+\label{subsec:euler_components}
+
+This use case includes two different components:
+
+\begin{description}
+	\item[The cli:]
+	\item[The EulerRoot TIP3-style contract:] Following the TIP3 conventions, this is the root contract to two types of leaves: EulerUser and EulerProblem.
+The EulerUser contract represents one user and the list of problems she has solved.
+The EulerProblem contract represents one problem and contains, among other things, the top ten leaderboard of the fastest solvers.
+\end{description}
 
@@
 \label{sec_three_paradigms}
-This contest has given us the opportunity to think harder about the types of use-cases of \zksnarks{} on blockchains.
+This contest has given us the opportunity to think harder about the categories of uses of \zksnarks{} on blockchains:
+\begin{enumerate}
+	\item Statically checking that someone has some information at their disposal(Euler case)
+	\item Encoding a possibly complex computation in a circuit and challenging a user with an instance of that computation (Sudoku case)
+	\item Using the \zksnark{} as an extension of the blockchain protocol itself (pincode, anonymous transactions, voting protocols)
+\end{enumerate}
+
+Of course, the boundaries between these categories may be blurred, but still they are meaningful.
+The point of the first category is that the data whose existence we are verifying is inert, static, it was chosen by the verifier according to some human meaning which is completely meaningless to the contract or the blockchain.
+In the second category, the value whose existence we are verifying has a computational (i.e.
+mathematical, see Section~\ref{subsec:math_enc}) meaning, and though this computational meaning\footnote{Of course, the answers to the Project Euler problems do have computational meaning ultimately, but no program is provided to encode the problem or check the solution.
+This computational meaning is inferred from the english description of the problem by the problem solver.} is not present on the blockchain itself, it is implicitly present in the verification key.
+Finally, the third category consists in the verification of data which has blockchain-protocol-level computational meaning (such as a public key).
+The privacy aspect of \zksnarks{}, which is of course the whole point, had initially hidden these distinctions from us.
+
+In category 1, the main advantage of \zksnarks{} is to not spoil the fun for other competitors.
+One must protect oneself from replay attacks (re-using the same zero-knowledge proof as some other competitor in order to pretend one has solved the problem) and brute-forcing the answer.
+
+In category 2, the point is to guarantee some mathematical properties of a wide range of submitted solutions to a given problem of a known computational nature, when not all of possible instances may be computed in advance.
+The \emph{zero-knowledge} part may or may not be important, but the \emph{succinct} part may well save some gas for cost-heavy verifications.
+
+In category 3, the zero-knowledge part plays a crucial part in preventing man-in-the-middle attacks for security-critical operations such as changing a lost public key in a wallet, or sending an anonymous amount of tokens to an anonymous recipient, or voting without revealing one's ballot.
+
+These three categories may be combined in several ways depending on the purpose.
 

### 2021-07-13 03_pincode/tests/00_init_sandbox.sh
Update 03_pincode tests

@@ -3,15 +3,17 @@
 . ./env.sh
 
 $FT switch to testnet
+$FT --switch sandbox1 node stop
 $FT switch remove sandbox1
 
 $FT switch create sandbox1 --image ocamlpro/nil-local-node || exit 2
 
-$FT node start
+$FT node start || exit 2
 
 echo Node is starting... waiting 10 seconds
 sleep 10
 
-$FT node give user0 --amount 100000
+$FT node give user0 user1 --amount 100000 || exit 2
+
 
 

### 2021-07-13 03_pincode/tests/01_prepare.sh

@@ -2,9 +2,10 @@
 
 . ./env.sh
 
-$FT exec -- ../cpp/pincode-client prepare toto
+$FT exec -- ../cpp/pincode-client prepare ${PINCODE_PASSPHRASE} || exit 2
 
-#$FT exec -- ../cpp/pincode-client prove toto '%{account:pubkey:user1}'
+zip provkey.bin.zip provkey.bin || exit 2
+
 
 # $FT contract deploy PubkeyRecovery --deployer user0 --credit 100 '{ "verifkey": "%{file:"'
 

### 2021-07-13 03_pincode/tests/02_deploy.sh

@@ -2,9 +2,7 @@
 
 . ./env.sh
 
-# $FT exec -- ../cpp/pincode-client prove toto '%{account:pubkey:user1}'
-
-$FT contract deploy PubkeyRecovery --deployer user0 --credit 100 '{ "verifkey": "%{file:verifkey.bin.hex}", "backup_key": "0x%{account:pubkey:user2}" }' -f
+$FT contract deploy PubkeyRecovery --sign user0 --deployer user0 --credit 100 '{ "verifkey": "%{file:verifkey.bin.hex}", "zip_provkey": "%{hex:file:provkey.bin.zip}", "backup_key": "0x%{account:pubkey:user2}" }' -f
 
 
 

### 2021-07-13 03_pincode/tests/03_get.sh

@@ -3,7 +3,7 @@
 . ./env.sh
 
 $FT call PubkeyRecovery get --local
-$FT call PubkeyRecovery pi_of_pubkey --local '{ "pubkey": "0x%{account:pubkey:user1}" }'
+$FT call PubkeyRecovery PrimaryInputOfPubkey --local '{ "pubkey": "0x%{account:pubkey:user1}" }'
 
 
 

### 2021-07-13 03_pincode/tests/04_replace.sh

@@ -2,10 +2,17 @@
 
 . ./env.sh
 
-$FT call PubkeyRecovery SetNewPubkey '{ "proof": "%{file:proof.bin.hex}", "newkey": "0x%{account:pubkey:user2}" }' --local
 
-# $FT multisig transfer 1 --from user0 --to PubkeyRecovery SetNewPubkey '{ "proof": "%{file:proof.bin.hex}", "newkey": "0x%{account:pubkey:user1}" }'
+$FT exec -- ../cpp/pincode-client prove "${PINCODE_PASSPHRASE}" '%{account:pubkey:user1}' || exit 2
 
+
+$FT call --local PubkeyRecovery Check '{ "proof": "%{file:proof.bin.hex}", "newkey": "0x%{account:pubkey:user1}" }' || exit 2
+
+
+
+$FT multisig transfer 1 --from user1 --to PubkeyRecovery SetFromPincode '{ "proof": "%{file:proof.bin.hex}", "newkey": "0x%{account:pubkey:user1}" }' --wait || exit 2
+
+$FT call --local PubkeyRecovery get
 
 
 

### 2021-07-13 03_pincode/tests/env.sh

@@ -17,3 +17,5 @@ function cmdk()
 
 FT="ft --echo"
 
+export PINCODE_PASSPHRASE=my-best-passphrase
+

### 2021-07-13 submission/submission.tex
prepare subsection for sudoku code
minor changes

@@
 
-\author{OCamlPro - Fabrice Le Fessant\footnote{Telegram: @fabrice\_dune} and Thomas Sibut-Pinote\footnote{Telegram: @ThomasSibutPinote}}
+\author{OCamlPro - Fabrice Le Fessant\footnote{Telegram: @fabrice\_dune} and Thomas Sibut-Pinote\footnote{Telegram: @ThomasSibutPinote} \\ \small{\url{https://github.com/OCamlPro/devex-18-zk-contest}}}
 \title{Groth16 zk-SNARK Proof Verification on Freeton : Three Use Cases}
+\date{}
 
@@
 
+\emph{Note: You may skip this section if you don't want to focus too much on the details on a first reading.}
+
 Let $n^2$ be the size of a Sudoku grid (in our case, $n=2$ and $n^2 = 4$ is the length of a side of the Sudoku square).In the following, the variables $(x_{i,j})_{0 \leq i,j < n^2}$ denote the (secret) values of the solution of a given instance of a Sudoku.
@@
 \end{description}
+
+\subsection{Code}
+\label{subsec:sudoku_code}
+
+TODO: code du sudoku ici
 

### 2021-07-13 bin/cli/test/circuit_test.cpp
uncomment 2^32-1 vote test case

@@ -44,7 +44,7 @@ BOOST_AUTO_TEST_CASE(circuit_test) {
 
     std::vector<field_type::value_type> hash_list {hashes[0],hashes[1],hashes[2],0,0,0,0,0,0,0};
 
-    std::vector<std::uint32_t> vote_choices {0,1,2,10000000/*,4294967295*/};
+    std::vector<std::uint32_t> vote_choices {0,1,2,10000000,4294967295};
     for(std::uint32_t vote_choice : vote_choices) {
         for(std::size_t secret_index = 0; secret_index < 4; ++secret_index) {
             std::vector<bool> vote_choice_bv(circuit::VOTE_MSG_LEN);

### 2021-07-13 bin/cli/test/circuit_test.cpp
split test cases to speed them up

@@ -45,8 +45,11 @@ BOOST_AUTO_TEST_CASE(circuit_test) {
     std::vector<field_type::value_type> hash_list {hashes[0],hashes[1],hashes[2],0,0,0,0,0,0,0};
 
     std::vector<std::uint32_t> vote_choices {0,1,2,10000000,4294967295};
-    for(std::uint32_t vote_choice : vote_choices) {
-        for(std::size_t secret_index = 0; secret_index < 4; ++secret_index) {
+    for(std::size_t index = 0; index < 4; ++index) {
+        field_type::value_type anoymous_id =
+            Hmac::get_hmac(secrets[index], std::vector<bool>(circuit::ANONYMOUS_ID_MSG_LEN, 1))[0];
+
+        for(std::uint32_t vote_choice : vote_choices) {
             std::vector<bool> vote_choice_bv(circuit::VOTE_MSG_LEN);
 
             for(std::size_t i = 0, temp = vote_choice; i < circuit::VOTE_MSG_LEN; ++i) {
@@ -55,33 +58,71 @@ BOOST_AUTO_TEST_CASE(circuit_test) {
             }
 
             field_type::value_type vote_choice_hmac =
-                Hmac::get_hmac(secrets[secret_index], vote_choice_bv)[0];
-            field_type::value_type anoymous_id =
-                Hmac::get_hmac(secrets[secret_index], std::vector<bool>(circuit::ANONYMOUS_ID_MSG_LEN, 1))[0];
+                Hmac::get_hmac(secrets[index], vote_choice_bv)[0];
 
-            for(std::size_t index = 0; index < circuit::MAX_VOTERS; ++index) {
-                for(int real_vote_hmac = 0; real_vote_hmac < 2; ++real_vote_hmac) {
-                    for(int real_anonymous_id  = 0; real_anonymous_id < 2; ++real_anonymous_id) {
-                        blueprint<field_type> bp = circuit::generate_circuit_with_witness<field_type>(
-                            hash_list,
-                            secrets[secret_index],
-                            vote_choice,
-                            index,
-                            real_vote_hmac ? vote_choice_hmac : hashes[0],
-                            real_anonymous_id ? anoymous_id : hashes[1]
-                        );
-                        if(secret_index!=3 &&
-                             index == secret_index &&
-                             real_vote_hmac &&
-                             real_anonymous_id) {
-                            BOOST_CHECK(bp.is_satisfied());
-                        } else {
[…]

### 2021-07-13 01_sudoku/cpp/sudoku.cpp
started adapting scripts and Makefile to the Sudoku case

@@ -21,36 +21,39 @@
 #include <nil/marshalling/status_type.hpp>
 
 #include "sudoku.hpp"
-#include "picosha2.h"
 #include <fstream>
+#include "picosha2.hpp"
 
 using namespace nil::crypto3::zk::snark;
 using namespace nil::crypto3::algebra;
 
 typedef algebra::curves::bls12<381> curve_type;
 typedef typename curve_type::scalar_field_type field_type;
-
 typedef zk::snark::r1cs_gg_ppzksnark<curve_type> scheme_type;
+using namespace std;
 
-void append_to_byteblob( std::vector<std::uint8_t> &byteblob, std::vector<std::uint8_t> bytes)
-{
-  byteblob.insert (byteblob.end(), bytes.begin(), bytes.end());
-}
+#include "utils.hpp"
 
-void binfile_of_byteblob( std::string file,  std::vector<std::uint8_t> byteblob ){
-  boost::filesystem::ofstream poutf( file );
-  for (const auto &v : byteblob) {
-    poutf << v;
-  }
-  poutf.close();
-}
 
-void hexfile_of_byteblob( std::string file,  std::vector<std::uint8_t> byteblob ){
-  std::string hex_str = picosha2::bytes_to_hex_string(byteblob.begin(), byteblob.end());
-  boost::filesystem::ofstream poutf( file );
-  poutf << hex_str << std::endl;
-  poutf.close();
-}
+// void append_to_byteblob( std::vector<std::uint8_t> &byteblob, std::vector<std::uint8_t> bytes)
+// {
+//   byteblob.insert (byteblob.end(), bytes.begin(), bytes.end());
+// }
+
+// void binfile_of_byteblob( std::string file,  std::vector<std::uint8_t> byteblob ){
+//   boost::filesystem::ofstream poutf( file );
+//   for (const auto &v : byteblob) {
+//     poutf << v;
+//   }
+//   poutf.close();
+// }
+
+// void hexfile_of_byteblob( std::string file,  std::vector<std::uint8_t> byteblob ){
+//   std::string hex_str = utils::bytes_to_hex_string(byteblob.begin(), byteblob.end());
+//   boost::filesystem::ofstream poutf( file );
+//   poutf << hex_str << std::endl;
+//   poutf.close();
+// }
 
 std::vector<int> read_input(std::string filename){
   std::vector<int> sudoku;
[…]

### 2021-07-13 01_sudoku/tests/01_prepare.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+. ./env.sh
+
+$FT exec -- ../cpp/sudoku-client --sudoku-generate-keys --proving-key-output ${SUDOKU_PROVKEY} --verification-key-output ${SUDOKU_VERIFKEY} || exit 2
+
+zip provkey.bin.zip ${SUDOKU_PROVKEY} || exit 2

### 2021-07-13 01_sudoku/tests/env.sh

@@ -1,0 +1,24 @@
+
+function cmd()
+{
+    echo
+    echo  COMMAND $*
+    echo
+    $* || exit 2
+}
+
+function cmdk()
+{
+    echo
+    echo  COMMAND $*
+    echo
+    $*
+}
+
+FT="ft --echo"
+
+
+export SUDOKU_INSTANCE=simple_instance.in
+export SUDOKU_SOLUTION=solved_instance.in
+export SUDOKU_PROVKEY=provkey.bin
+export SUDOKU_VERIFKEY=verifkey.bin

### 2021-07-13 submission/submission.tex
minor changes in submission

@@
 
-The previous example is somewhat limited by the fact that Sudokus are easily solvable problems, either by hand or with a computer; they are not a realistic use case of \zksnarks{}\footnote{Although they hint at a possible use for \zksnarks{}: checking a result without implementing its full logic in Solidity may save precious storage and computations on the blockchain}.
+The previous example is somewhat limited by the fact that Sudokus are easily solvable problems, either by hand or with a computer; they are not a realistic use case of \zksnarks{}\footnote{Although they hint at a possible use for \zksnarks{}: checking a result without implementing its full logic in Solidity may save precious storage and computations on the blockchain.}.
 
@@
 
-Project Euler is sort of a gentlemen's competition.
-For example, competitors are supposed to have found the answer using a program running at most in one minute, but no mechanism enforces this.
-Still, some protections are in place, partly to enforce the spirit of the competition, and partly because of past abuse.
-For instance, a captcha system prevents one from attempting many solutions in a row.
-We decided to emulate the latter mechanism.
-If we simply gave a proving key to try and find the actual solution to the problem, users might be tempted to try to build a proof using every single integer until it works\footnote{We have noticed that although generating a correct proof may take time, an incorrect input is usually rejected in less than one second.}.
-Hence, the value they must find is actually
+Project Euler is a gentlemen's competition. For example, competitors
+are supposed to have found the answer using a program running at most
+in one minute, but no mechanism enforces this. Still, some protections
+are in place, partly to enforce the spirit of the competition, and
+partly because of past abuse. For instance, a captcha system prevents
+one from attempting many solutions in a row. We decided to emulate the
+latter mechanism. If we simply gave a proving key to try and find the
+actual solution to the problem, users might be tempted to try to build
+a proof using every single integer until it works\footnote{We have
+  noticed that although generating a correct proof may take time, an
+  incorrect input is usually rejected in less than one
+  second.}. Hence, the value they must find is actually
 \[ \textrm{SHA256}^{1\,000\,000}\left(problem\_number | solution | nonce\right)\]

### 2021-07-13 02_euler/tests/02_deploy.sh
Update Makefiles and document contracts

@@ -2,9 +2,9 @@
 
 . ./env.sh
 
-$FT contract deploy EulerRoot --deployer user0 --credit 2 '{ "problem_code": "%{get-code:contract:tvc:EulerProblem}", "user_code": "%{get-code:contract:tvc:EulerUser}" }' -f || exit 2
+$FT contract deploy EulerRoot --deployer user0 --credit 3 '{ "problem_code": "%{get-code:contract:tvc:EulerProblem}", "user_code": "%{get-code:contract:tvc:EulerUser}" }' -f || exit 2
 
-$FT account info EulerRoot
+$FT account info EulerRoot || exit 2
 
 $FT call --local EulerRoot get || exit 2
 

### 2021-07-13 02_euler/tests/03_new_problem.sh

@@ -4,7 +4,7 @@
 
 $FT call EulerRoot new_problem '{ "problem": %{env:EULER_PROBLEM}, "verifkey": "%{file:verifkey.bin.hex}", "zip_provkey": "%{hex:file:provkey.bin.zip}", "nonce": "%{env:EULER_NONCE}", "title": "%{hex:string:Example}", "description": "%{hex:string:a very basic example}", "url": "%{hex:string:https://euler.org/}" }' --wait || exit 2
 
-$FT account info EulerRoot
+$FT account info EulerRoot || exit 2
 
 rm -f euler_problem.addr
 $FT call --local EulerRoot problem_address '{ "problem": %{env:EULER_PROBLEM} }' --subst @%{res:addr} --output euler_problem.addr || exit 2

### 2021-07-14 01_sudoku/tests/convert_instance.sh
finally working matrix input converter

@@ -2,18 +2,20 @@
 
 SUDOKU_SIZE=$(wc -l < "$1")
 IFS='' read -r -d '' string < $1
-#string=tr -d ' ' $string
+string=${string//$'\n'/}
 res=""
 re='^[1-9]'
 for (( i=0; i <$SUDOKU_SIZE; i++ )); do
     for (( j=0; j <$SUDOKU_SIZE; j++ )); do
 	let index=i*$SUDOKU_SIZE+j
-	if [[ '${string:$index:1}' != 0 ]]; then
-	    res="$res, { \"i\" : \"$i\",\"j\" : \"$j\", \"value\" : \"${string:$index:1}\"}"
-	else
-	    echo ${string:$index:1}
+	if [ "${string:$index:1}" != "0" ]; then
+	    if [[ -z "$res" ]]; then
+		sep=""
+	    else
+		sep=","
+	    fi
+	    res="$res$sep { \"i\" : \"$i\",\"j\" : \"$j\", \"value\" : \"${string:$index:1}\"}"
         fi
-
     done
 done
 

### 2021-07-14 01_sudoku/tests/03_new_instance.sh
script for submitting new instance in tests

@@ -1,0 +1,11 @@
+#!/bin/bash
+
+. ./env.sh
+
+INSTANCE=$(./convert_instance.sh new_instance.in)
+
+$FT multisig transfer --from user0 --to  sudoku 1 submit_instance '{ "instance" : ['"${INSTANCE}"']}' --wait || exit 2
+
+# $FT multisig transfer --from user0 --to  sudoku 1 submit_instance '{ "instance" : [{ "i" : "3", "j" : "3", "value" : "4"},{ "i" : "2", "j" : "3", "value" : "1"}]}' --wait || exit 2
+
+$FT account info sudoku

### 2021-07-14 02_euler/tests/07_submit_user3.sh
Tests works with docker ft

@@ -9,6 +9,6 @@ $FT call --local euler_problem get
 
 # wrong solution:
 
-$FT exec -- ../cpp/euler-client prove ${EULER_PROBLEM} ${EULER_NONCE}  ${EULER_SOLUTION}0 '%{account:pubkey:user3}' && echo OK
+cmdk ../cpp/euler-client prove ${EULER_PROBLEM} ${EULER_NONCE}  ${EULER_SOLUTION}0 $($FT output '%{account:pubkey:user3}') 
 
 $FT call --local euler_problem get    

### 2021-07-14 03_pincode/tests/01_prepare.sh

@@ -2,11 +2,6 @@
 
 . ./env.sh
 
-$FT exec -- ../cpp/pincode-client prepare ${PINCODE_PASSPHRASE} || exit 2
+cmd ../cpp/pincode-client prepare ${PINCODE_PASSPHRASE} || exit 2
 
 zip provkey.bin.zip provkey.bin || exit 2
-
-
-# $FT contract deploy PubkeyRecovery --deployer user0 --credit 100 '{ "verifkey": "%{file:"'
-
-

### 2021-07-14 03_pincode/tests/04_replace.sh

@@ -3,10 +3,10 @@
 . ./env.sh
 
 
-$FT exec -- ../cpp/pincode-client prove "${PINCODE_PASSPHRASE}" '%{account:pubkey:user1}' || exit 2
+cmd ../cpp/pincode-client prove "${PINCODE_PASSPHRASE}" $($FT output '%{account:pubkey:user1}') || exit 2
 
 
-$FT call --local PubkeyRecovery Check '{ "proof": "%{file:proof.bin.hex}", "newkey": "0x%{account:pubkey:user1}" }' || exit 2
+#$FT call --local PubkeyRecovery Check '{ "proof": "%{file:proof.bin.hex}", "newkey": "0x%{account:pubkey:user1}" }' || exit 2
 
 
 

### 2021-07-14 submission/submission.tex
Update of section 4 pincode

@@
 In this use case, we use \zksnarks{} to allow users to replace their
-public keys in multisig wallets. The typical use is when a user has
-lost the associated secret key, and is unable to sign/confirm any new
-transaction. With our approach, the user first creates a recovery
-contract, where a passphrase is associated to his public key. If he
-needs to change his public key, he can use \zksnarks{} to associate a new
-public key in his recovery contract, and tell multisig wallets to
-safely replace his pubkey by the new one.
+public keys in other contracts, for example multisig wallets. The
+typical use is when a user has lost the associated secret key, and is
+unable to sign/confirm any new transaction. With our approach, the
+user first creates a recovery contract, where a passphrase is
+associated to his public key. If he needs to change his public key, he
+can use \zksnarks{} to associate a new public key in his recovery
+contract, and tell other contracts to safely replace his pubkey by the
+new one.
 
@@
   (based on hashes for example) give an opportunity for
-  man-in-the-middle attacks ;
+  man-in-the-middle attacks;
 \item As the user does not disclose his passphrase, the pubkey can be
-  replaced several times ;
+  replaced several times;
 \item The user does not need to create the new public key ahead of
   time. Instead, he can create it when he has lost the former one,
-  decreasing the likelihood of losing the associated secret key also ;
+  decreasing the likelihood of losing the associated secret key also;
 \end{itemize}
@@
    contract, and a file \lstinline{provkey.hex} that can be used to
-   create new witnesses ;
+   create new witnesses;
  \item To create a witness that the passphrase is known when providing
@@
   \end{itemize}
-\item[PubkeyRecovery smart contract:] This smart contract is a TIP-3
-  contract, using the initial public key to verify its address. This
-  contract is very simple. It contains:
+\item[PubkeyRecovery smart contract:] This smart contract is a
+  contract à la TIP-3 contract, using the initial public key to verify
+  its address. This contract is very simple. It contains:
   \begin{itemize}
   \item A constructor to set the circuit that will be used to verify
-    that the passphrase is known when it is used ;
+    that the passphrase is known when it is used;
   \item An external function
-    \lstinline{SetNewPubkey(bytes proof, uint256 pubkey)}
+    \lstinline{SetFromPincode(bytes proof, uint256 pubkey)}
     to define the new public key, while providing a
-    proof of knowledge of the passphrase ;
+    proof of knowledge of the passphrase;
   \item An external function
-    \lstinline{RecoverPubkey(address multisigaddr)}
-    to call a multisig contract to update the
-    corresponding custodian. The multisig contract will verify that
-    the address is correct before replacing the public key ;
+    \lstinline{RecoverPubkey(RecoverablePubkey addr)} to call a
+    recoverable contract to update the corresponding pubkey.
   \end{itemize}
-\item[Modified Multisig Wallet:] This is a standard multisig wallet,
-  modified to recognize addresses of \lstinline{PubkeyRecovery} smart
-  contracts. They provide two additionnal functions:
+\item[Abstract RecoverablePubkey contract:] This is an abstract
+  contract, from which other contracts should inherit to be able to
+  benefit from the {\tt PubkeyRecovery} mechanism. The contract
+  provides two main functions:
   \begin{itemize}
-  \item An external function
-    \lstinline{SetPubkeyRecoveryCode(TvmCell code)}
-    to define the code of the \lstinline{PubkeyRecovery} smart
-    contract. Because the code hash is known, anybody can call this
-    function with the correct code.
-  \item An external function
-    \lstinline{RecoverPubkey(uint256 oldkey, uint256 newkey)}
-    that can only be called by a
-    \lstinline{PubkeyRecovery} smart contract.
+  \item An external function \lstinline{SetPubkeyRecoveryCode(TvmCell
+    code)} to define the code of the \lstinline{PubkeyRecovery} smart
+    contract. Because the code hash is known (inlined in the code),
+    anybody can call this function with the correct code.
+  \item An external function \lstinline{RecoverPubkey(uint256 oldkey,
+    uint256 newkey)} that can only be called by a
+    \lstinline{PubkeyRecovery} smart contract. The function verifies
+    that the address belongs to such a contract before calling a
+    function \lstinline{recover\_pubkey(oldkey, newkey)}, that the
+    inheriting contract should define to specify the business logic
+    that should happen when a pubkey is replaced.
   \end{itemize}
+\item[Modified Multisig Wallet:] The
+  \lstinline{RecoverableMultisigWallet} contract is the standard
+  multisig wallet of Surf, updated for version 0.40 of Solidity, and
+  modified to inherit from the \lstinline{RecoverablePubkey}
+  contract. It defines the business logic to replace a custodian key.
+  For that, it first checks that the old key belongs to an existing
+  custodian of the contract, that the new key does not belong to an
+  existing custodian, and then replace the old key by the new one,
+  associated to the same index (for bitfields).
 \end{description}
@@
 \item The interface has been improved to provide multiple levels of
-  subcommands, making them easier to understand and to use ;
+  subcommands, making them easier to understand and to use;
 \item A new argument {\tt --image} is available with {\tt ft switch

### 2021-07-14 03_pincode/tests/04_replace.sh

@@ -6,7 +6,7 @@
 cmd ../cpp/pincode-client prove "${PINCODE_PASSPHRASE}" $($FT output '%{account:pubkey:user1}') || exit 2
 
 
-#$FT call --local PubkeyRecovery Check '{ "proof": "%{file:proof.bin.hex}", "newkey": "0x%{account:pubkey:user1}" }' || exit 2
+$FT call --local PubkeyRecovery Check '{ "proof": "%{file:proof.bin.hex}", "newkey": "0x%{account:pubkey:user1}" }' || exit 2
 
 
 

### 2021-07-14 01_sudoku/cpp/main.cpp
Changes to Sudoku Cpp, solidity and scripts to be able to submit new instance

@@ -56,7 +56,7 @@ typedef zk::snark::r1cs_gg_ppzksnark<curve_type> scheme_type;
 
 int main(int argc, char *argv[]) {
   string instance_filename, solution_filename,
-    proving_key_output_filename,verification_key_output_filename ;
+    proving_key_filename,verification_key_filename ;
     boost::program_options::options_description options(
         "R1CS Generic Group PreProcessing Zero-Knowledge Succinct Non-interactive ARgument of Knowledge "
         "(https://eprint.iacr.org/2016/260.pdf) CLI Proof Generator");
@@ -68,8 +68,8 @@ int main(int argc, char *argv[]) {
       ("sudoku-generate-proof","generate Sudoku proof for one solved instance")
       ("instance,inst", boost::program_options::value<std::string>(&instance_filename)->default_value("simple_instance.in"))
       ("solution,sol", boost::program_options::value<std::string>(&solution_filename)->default_value("solved_instance.in"))
-      ("proving-key-output,pko", boost::program_options::value<std::string>(&proving_key_output_filename)->default_value("provkey.bin"))
-      ("verification-key-output,pko", boost::program_options::value<std::string>(&verification_key_output_filename)->default_value("verifkey.bin"));
+      ("proving-key-filename,pko", boost::program_options::value<std::string>(&proving_key_filename)->default_value("provkey.bin"))
+      ("verification-key-filename,pko", boost::program_options::value<std::string>(&verification_key_filename)->default_value("verifkey.bin"));
     // ("proof-output,po", boost::program_options::value<boost::filesystem::path>(&pout)->default_value("proof"))
     // ("proving-key-output,pko", boost::program_options::value<boost::filesystem::path>(&pkout)->default_value("pkey"))
     // ("verifying-key-output,vko", boost::program_options::value<boost::filesystem::path>(&vkout)->default_value("vkey"));
@@ -85,7 +85,7 @@ int main(int argc, char *argv[]) {
     }
 
     if (vm.count("sudoku-generate-keys")) {
-        generate_keys(proving_key_output_filename,verification_key_output_filename);
+        generate_keys(proving_key_filename,verification_key_filename);
     };
 
     // if (vm.count("sudoku-verify-proof")){
@@ -100,7 +100,7 @@ int main(int argc, char *argv[]) {
       // std::cout << "Please input the sudoku solved instance (default is in file solved_instance.in)" << std::endl;
       // std::cin >> solution_filename;
[…]

### 2021-07-14 01_sudoku/tests/01_prepare.sh

@@ -2,6 +2,6 @@
 
 . ./env.sh
 
-$FT exec -- ../cpp/sudoku-client --sudoku-generate-keys --proving-key-output ${SUDOKU_PROVKEY} --verification-key-output ${SUDOKU_VERIFKEY} || exit 2
+$FT exec -- ../cpp/sudoku-client --sudoku-generate-keys --proving-key-filename ${SUDOKU_PROVKEY} --verification-key-filename ${SUDOKU_VERIFKEY} || exit 2
 
-zip provkey.bin.zip ${SUDOKU_PROVKEY} || exit 2
+zip ${SUDOKU_ZIPPED_PROVKEY} ${SUDOKU_PROVKEY} || exit 2

### 2021-07-14 01_sudoku/tests/convert_instance.sh

@@ -14,7 +14,7 @@ for (( i=0; i <$SUDOKU_SIZE; i++ )); do
 	    else
 		sep=","
 	    fi
-	    res="$res$sep { \"i\" : \"$i\",\"j\" : \"$j\", \"value\" : \"${string:$index:1}\"}"
+	    res="$res$sep [\"$i\",\"$j\",\"${string:$index:1}\"]"
         fi
     done
 done

### 2021-07-14 01_sudoku/tests/env.sh

@@ -21,4 +21,5 @@ FT="ft --echo"
 export SUDOKU_INSTANCE=simple_instance.in
 export SUDOKU_SOLUTION=solved_instance.in
 export SUDOKU_PROVKEY=provkey.bin
+export SUDOKU_ZIPPED_PROVKEY=provkey.bin.zip
 export SUDOKU_VERIFKEY=verifkey.bin

### 2021-07-14 03_pincode/cpp/utils.hpp

@@ -193,3 +193,41 @@ void save_big_proof( std::string file,
  
  binfile_of_byteblob( file, byteblob );
 }
+
+
+// This function translates a bytes[32] vector into a uint32[4]
+// vector, by keeping only the first 16 bytes, and removing one bit to
+// remain positive.  The result is only 124 bits long, but it's enough
+// to keep finding collisions computationnaly impossible.
+void uint32s_of_bytes( std::vector<uint32_t> &uints, std::vector<uint8_t> &bytes )
+{
+  for( int i = 0 ; i<4; i++ ){
+    uints[i] =
+      ( (uint32_t) bytes[ 4*i] ) +
+      ( ( (uint32_t) bytes[ 4*i+1 ] ) << 8 ) +
+      ( ( (uint32_t) bytes[ 4*i+2 ] ) << 16 ) +
+      ( ( (uint32_t) bytes[ 4*i+3 ] & 0x7f ) << 24 ) ;
+  }
+}
+
+
+void uint32s_of_passphrase( std::vector<uint32_t> &uints, std::string passphrase ){
+
+  std::vector<uint8_t> hash(picosha2::k_digest_size);
+
+  picosha2::hash256( passphrase.begin(), passphrase.end(), hash.begin(), hash.end());
+  uint32s_of_bytes( uints, hash );
+}
+
+
+void uint32s_of_pubkey( std::vector<uint32_t> &uints, std::string pubkey_s ){
+
+  std::vector<uint8_t> pubkey(32);
+
+  for( int i = 0 ; i < 32 ; i++ ){
+    pubkey[ i ] = int_of_hexchar( pubkey_s[ i*2 ] ) * 16 + int_of_hexchar( pubkey_s[ i*2+1 ] ) ;
+    // cerr << pubkey [ i ] << endl ;
+  }
+  uint32s_of_bytes( uints, pubkey );
+}
+

### 2021-07-14 submission/submission.tex
remove old script + changes to submission after call with Fabrice

--- 2021-07-13 submission/submission.tex
@@
 
-	\item[Marshalling and memory corruption:] Because of a memory corruption error in the marshalling of the verification key, we were unable to do a full 9 by 9 Sudoku, restricting ourselves to 4 by 4.
-All our code is generic (it is generated from an OCaml program which takes as a parameter the value $n$ such that the Sudoku is $n^2$ by $n^2$).
-We were told that after the contest, a more robust marshalling library would be provided.
-In any case we would be glad to discuss this issue with the Nil foundation team to give users the full Sudoku experience!
-In the meantime, a 4 by 4 Sudoku is sufficient to get a sense of the dynamics of \zksnark-based Sudoku.
+	\item[Marshalling and memory corruption:] Because of a memory
+          corruption error in the marshalling function (in the code
+          provided for the contests) of the verification key, we were
+          unable to do a full 9 by 9 Sudoku, restricting ourselves to
+          4 by 4. All our code is generic (it is generated from an
+          OCaml program which takes as a parameter the value $n$ such
+          that the Sudoku is $n^2$ by $n^2$). We were told that after
+          the contest, a more robust marshalling library would be
+          provided. In any case we would be glad to discuss this issue
+          with the Nil foundation team to give users the full Sudoku
+          experience! In the meantime, a 4 by 4 Sudoku is sufficient
+          to get a sense of the dynamics of \zksnark-based Sudoku.
 
@@
 
-As mentioned in Section \ref{subsec:general_remarks}, we had to restrict ourselves to a 4 by 4 Sudoku grid, even though our code generator is generic in the grid size.
-This is because the marshalling function on the 9 by 9 code produced a memory corruption error.
+As mentioned in Section \ref{subsec:general_remarks}, we had to
+restrict ourselves to a 4 by 4 Sudoku grid, even though our code
+generator is generic in the grid size. This is because the marshalling
+function (in the codep rovided for the contest) on the 9 by 9 code
+produced a memory corruption error.
 
@@
 \item[The cli:] it is a C++ program linked to the Blueprint \zksnarks{} library. It can be used in two different ways:
+
+  TODO: mettre un exemple
+  copier coller la commande
+
 	\begin{itemize}
@@
     \end{lstlisting}
-    It will check the input proof against the verification key \lstinline[language=Solidity]|v_key| and the current instance \lstinline[language=Solidity]|m_instance|, both local to the contract.
-This instance is stored as an array of \lstinline[language=Solidity]|fixed_value|:
+    It will check the input proof against the verification key
+    \lstinline[language=Solidity]|v_key| and the current instance
+    \lstinline[language=Solidity]|m_instance|, which are both local to
+    the contract and set in the constructor. This instance is stored
+    as an array of \lstinline[language=Solidity]|fixed_value|:
     \begin{lstlisting}[language=Solidity]
@@
 \end{description}
-
-\subsection{Code}
-\label{subsec:sudoku_code}
-
-TODO: code du sudoku ici
 
@@
   (based on hashes for example) give an opportunity for
-  man-in-the-middle attacks ;
+  man-in-the-middle attacks;
 \item As the user does not disclose his passphrase, the pubkey can be
-  replaced several times ;
+  replaced several times;
 \item The user does not need to create the new public key ahead of
   time. Instead, he can create it when he has lost the former one,
-  decreasing the likelihood of losing the associated secret key also ;
+  decreasing the likelihood of losing the associated secret key also.
 \end{itemize}

### 2021-07-14 01_sudoku/tests/03_new_instance.sh

@@ -1,11 +1,0 @@
-#!/bin/bash
-
-. ./env.sh
-
-INSTANCE=$(./convert_instance.sh new_instance.in)
-
-$FT multisig transfer --from user0 --to  sudoku 1 submit_instance '{ "instance" : ['"${INSTANCE}"']}' --wait || exit 2
-
-# $FT multisig transfer --from user0 --to  sudoku 1 submit_instance '{ "instance" : [{ "i" : "3", "j" : "3", "value" : "4"},{ "i" : "2", "j" : "3", "value" : "1"}]}' --wait || exit 2
-
-$FT account info sudoku

### 2021-07-14 submission/submission.tex

--- 2021-07-14 submission/submission.tex
@@
   time. Instead, he can create it when he has lost the former one,
-  decreasing the likelihood of losing the associated secret key also;
+
+  decreasing the likelihood of losing the associated secret key also.
 \end{itemize}
@@
   \begin{itemize}
-  \item An external function \lstinline{SetPubkeyRecoveryCode(TvmCell
-    code)} to define the code of the \lstinline{PubkeyRecovery} smart
+  \item An external function \lstinline{SetPubkeyRecoveryCode(TvmCellcode)} to define the code of the \lstinline{PubkeyRecovery} smart
     contract. Because the code hash is known (inlined in the code),
     anybody can call this function with the correct code.
-  \item An external function \lstinline{RecoverPubkey(uint256 oldkey,
-    uint256 newkey)} that can only be called by a
+  \item An external function \lstinline{RecoverPubkey(uint256 oldkey,uint256 newkey)} that can only be called by a
     \lstinline{PubkeyRecovery} smart contract. The function verifies

### 2021-07-14 submission/submission.tex
update submission with Euler and Sudoku parts

@@
 \begin{description}
-	\item[Code:] All our code comes with a README and tests.
-This document is provided as an overview of our use cases for \zksnarks{} on the Freeton blockchain but you can also directly plunge into the code.
-All our code is under the GPL license and is hosted at \url{https://github.com/OCamlPro/devex-18-zk-contest}.
+	\item[Code:] All our code comes with a README, standard
+          in-code documentation and tests. This document is provided
+          as an overview of our use cases for \zksnarks{} on the
+          Freeton blockchain but you can also directly dive into the
+          code. All our code is under the GPL license and is hosted at
+          \url{https://github.com/OCamlPro/devex-18-zk-contest}.
 
@@
 
-	\item[Keys on contracts: ] For all of our smart contracts, we provided, along with the verification key as needed by the \verb|vergroth16| instruction, the proving key (in a zipped) on the smart contract.
-This enables users to easily find it in order to generate their proofs.
-In case the contract deployer should decide to keep the possibility of changing the verification and proving keys of the problem(s), this also makes it easiest to follow changes before submitting a solution.
+	\item[Keys on contracts: ] In the Euler and Pincode smart
+          contracts, we provided, along with the verification key as
+          needed by the \verb|vergroth16| instruction, the proving key
+          (in a zipped format) on the smart contract. This enables
+          users to easily find it in order to generate their
+          proofs. In case the contract deployer should decide to keep
+          the possibility of changing the verification and proving
+          keys of the problem(s), this also makes it easiest to follow
+          changes before submitting a solution. Unfortunately, the
+          proving key for the Sudoku has size 64KB (19KB after
+          compression) which is about 6 times (respectively 10 times
+          once zipped) bigger than for Euler and Pincode, and we
+          decided not to include it.
 
@@
 
-\section{A toy example: Sudoku}
+\section{A toy example: the Sudoku grid}
 \label{section_sudoku}
@@
 
-Let's start with our first toy use case.
-Suppose you want to set up a Sudoku problem for your students to solve, so that upon completion they receive some token.
-The issue is that once any student has solved it, the solution sits on the blockchain for all to see.
-All the other students can cheat by copying it, instead of doing the work by themselves, which defeats the whole purpose.
+Let's start with our first toy use case. Suppose you want to set up a
+Sudoku problem for your students to solve, so that upon completion
+they receive some token. The issue is that once any student has solved
+it, the solution sits on the blockchain for all to see. All the other
+students can cheat by copying it, instead of doing the work by
+themselves, which defeats the whole purpose.
 
@@
 
-\emph{Note: You may skip this section if you don't want to focus too much on the details on a first reading.}
+\emph{Note: This section may be skipped upon a first reading without
+  loss of information.}
 
-Let $n^2$ be the size of a Sudoku grid (in our case, $n=2$ and $n^2 = 4$ is the length of a side of the Sudoku square).In the following, the variables $(x_{i,j})_{0 \leq i,j < n^2}$ denote the (secret) values of the solution of a given instance of a Sudoku.
-The variables $(f_{i,j})_{0 \leq i,j < n^2}$ denote the instance so that
+Let $n^2$ be the size of a Sudoku grid (in our case, $n=2$ and $n^2 =
+4$ is the length of a side of the Sudoku square).In the following, the
+variables $(x_{i,j})_{0 \leq i,j < n^2}$ denote the (secret) values of
+the solution of a given instance of a Sudoku. The variables
+$(f_{i,j})_{0 \leq i,j < n^2}$ denote the instance so that
 \begin{equation}
@@
 \end{equation}
-The (well-known) constraints of a Sudoku are encoded by the following equations:
+The (well-known) constraints of a Sudoku are encoded by the following
+equations:
 \[ \prod_{k=1}^{n^2} \left( x_{i,j} - k \right) = 0 \textrm{ for all $0 \leq i,j < n^2$} \]
@@
 \[ f_{i,j} x_{i,j} = f_{i,j}^2 \textrm{ for all $0 \leq i,j < n^2$}\]
-and, for all $S$ set of indices representing a row, a column or a box as per the rules of Sudoku:
+and, for all $S$ set of indices representing a row, a column or a box
+as per the rules of Sudoku:
 \[ \prod_{(i,j) \in S} x_{i,j} = \prod_{k=1}^{n^2} k = \left(n^2\right)! \; .\]
 
-The first equations guarantee that the only permitted values for $x_{i,j}$ are the integers from $1$ through $n^2$, while the second force
+The first equations guarantee that the only permitted values for
+$x_{i,j}$ are the integers from $1$ through $n^2$, while the second
+force
 
@@
 
-  TODO: mettre un exemple
-  copier coller la commande
-
 	\begin{itemize}
 	\item To create the original proving and verification keys. This step is independent of any given Sudoku instance and should only be done once.
-		\item To generate a proof given an instance and a solution. The instance is given as a text file such as
+              \begin{verbatim}
+              ./sudoku-client --sudoku-generate-keys
+              \end{verbatim}
+	    \item To generate a proof given an instance and a solution.
+              \begin{verbatim}
+              ./sudoku-client --sudoku-generate-proof --instance
+                instance.in --solution solution.in
+              \end{verbatim}
+              The instance is given as a text file such as
 
@@
 	\end{itemize}
-    \item[The Sudoku smart contract:] The main function of this smart contract is
-    \begin{lstlisting}[language=Solidity]
-    function submit(bytes proof)
-        public view returns (bool res, string blob_str)
-    \end{lstlisting}
-    It will check the input proof against the verification key
-    \lstinline[language=Solidity]|v_key| and the current instance
-    \lstinline[language=Solidity]|m_instance|, which are both local to
-    the contract and set in the constructor. This instance is stored
-    as an array of \lstinline[language=Solidity]|fixed_value|:
-    \begin{lstlisting}[language=Solidity]
-    struct fixed_value {
-      uint8 i;
-      uint8 j;
-      uint8 value;
-    }
+      \item[The Sudoku smart contract:] The only contract for this use
+        case is the \verb|Sudoku| contract. Only the deployer's public
+        key is allowed to submit new Sudoku instances. Its constructor
+        defines an initial instance and the verification key (in this
+        case the proving key is not included in the smart contract due
+        to its size). The main function \verb|submit| takes as input a
+        proof and returns a boolean stating its correctness. The local
+        function \verb|pi_from_instance| encodes the primary input
+        given the current instance, but does not store it
+        anywhere. The \verb|submit_instance| allows the owner to add a
+        new challenge at any time.
 
@@
 
-The previous example is somewhat limited by the fact that Sudokus are easily solvable problems, either by hand or with a computer; they are not a realistic use case of \zksnarks{}\footnote{Although they hint at a possible use for \zksnarks{}: checking a result without implementing its full logic in Solidity may save precious storage and computations on the blockchain.}.
+The previous example is somewhat limited by the fact that Sudokus are
+easily solvable problems, either by hand or with a computer; they are
+not the most convincing use case of (at least the zero-knowledge
+aspect of) \zksnarks{}\footnote{Although they hint at a possible use
+  for \zksnarks{}: checking a result without implementing its full
+  logic in Solidity may save precious storage and computations on the
+  blockchain.}.
 
@@
 
+\subsection{Components}
+\label{subsec:euler_components}
+
+This use case includes two different components:
+
+\begin{description}
+	\item [The C++ client]
+	The `euler-client` program can be used in 2 ways:
+	\begin{enumerate}
+		\item \begin{verbatim}
+		./euler-client prepare PROBLEM NONCE SOLUTION
+		\end{verbatim}, where \verb|PROBLEM| is
+		a problem number, \verb|NONCE| is an arbitrary number different for every
+		problem, and \verb|SOLUTION| is the numeric solution, will generate a
+		proving key and a verification key for the problem and its solution. These files can be published for users to propose submissions and to verify them.
+
+		\item \begin{verbatim}
+		./euler-client prove PROBLEM NONCE SUBMISSION PUBKEY
+		\end{verbatim}, where
+		\verb|SUBMISSION| is the numeric solution proposed by the user and
+		\verb|PUBKEY| is his own public key (to prevent other users from
+		submitting the same solution). The program 	generates a proof to be then
+		submitted online.
+	\end{enumerate}
+
+	\item[Solidity Smart Contracts] The Solidity smart contracts are located in the `contracts/`
+	directory. They can be built with `make` if `ft` (freeton-wallet) is
+	installed.
+
+	The following smart contracts are defined:
+        \begin{enumerate}
+
+	\item \verb|EulerRoot| : it's the central contract of a set of
+        Euler problems. The \verb|EulerRoot| contracts is owned by the
+        organizer, who is the only one able to publish new Euler
+        problems.  Its most important functions are
+        \verb|new_problem()| to deploy a new problem contract,
+        \verb|new_user()| to deploy a user contract (anybody can call
+        it) and \verb|submit()| to submit a solution for a
+        problem. \verb|problem_address()| and \verb|user_address()|
+        are useful to get the contract address of a problem or a
+        user. An event is emitted everytime a problem is solved by a
+        user.
+
+	\item \verb|EulerProblem|: it's the contract corresponding to a
+        given Project Euler problem. The contract contains the
+        verification key of the problem, so that it can check the
+        proofs submitted by users. Since proofs are attached to users'
+        pubkeys, other users cannot re-use proofs submitted by other
+        users. Each \verb|EulerProblem| contract contains the top 10
+        of the first users to submit a correct solution. An event is
+        also emitted everytime the problem is solved by a user. The
+        contract also contains the description of the problem (title,
+        description, url) and the information needed to submit
+        solutions (compressed proving key and nonce).
+
+	\item \verb|EulerUser|: it's the contract corresponding to the
+        pubkey of a user. The user can provide a name using the
+        \verb|set_name()| function.  The \verb|has_solved()| function
+        is called by the \verb|EulerRoot| contract when the user has
+        solved a new problem. The function stores the problem and the
+        time of solution in the contract.
+
+	For internal messages between these contracts, they either check that
+	messages are coming from the unique \verb|EulerRoot| contract, or that they
+	come from pre-computed addresses à la TIP-3.
+
+\end{description}
+
 \subsection{Brute-force protection}
 \label{subsec:brute-force}
+\emph{This small section details an interesting aspect we had to
+  develop to prevent bruteforce attacks.}
 
@@
 
-\subsection{Components}
-\label{subsec:euler_components}
+To prevent users from easily brute-forcing the numeric solutions, we
+added a simple proof of work of about 20 seconds. The proof of work is
+based on 1,000,000 iterations of sha256 over the concatenation of the
+problem number, the nonce and the solution. Since a random nonce
+included in the hash, the proof-of-work cannot be done before the new
+problem has been submitted and the corresponding new nonce published.
 
-This use case includes two different components:
-
-\begin{description}
-	\item[The cli:]
-	\item[The EulerRoot TIP3-style contract:] Following the TIP3 conventions, this is the root contract to two types of leaves: EulerUser and EulerProblem.
+%\begin{description}
+%	\item[The cli:]
+%	\item[The EulerRoot TIP3-style contract:] Following the TIP3 conventions, this is the root contract to two types of leaves: EulerUser and EulerProblem.
 The EulerUser contract represents one user and the list of problems she has solved.
 The EulerProblem contract represents one problem and contains, among other things, the top ten leaderboard of the fastest solvers.
-\end{description}
+%\end{description}
 
@@
     should be called as:
-\begin{verbatim}
+\begin{lstlisting}
 pincode-client prepare "my pass phrase"
-\end{verbatim}
+\end{lstlisting}
    This will generate a file \lstinline{verifkey.hex} that can be used

### 2021-07-14 submission/submission.tex
add pincode image, early pointers to ft

@@
 \begin{description}
+        \item[ft:] Throughout this project, we make heavy use of our
+          in-house freeton wallet and client \verb|ft|. We have taken
+          extra care to make its use very simple, using docker images
+          and intuitive, well-documented features. We have specially
+          adapted this tool to be able to create local sandboxes using
+          the Nil Foundation's fork of the TON OS, as well as to
+          interact with the Nil foundation server. Please check out
+          \url{https://hub.docker.com/r/ocamlpro/ft}. The
+          documentation is available both in the command line through
+          \verb|ft --help| and on the website
+          \url{https://ocamlpro.github.io/freeton_wallet/sphinx/}.
+
 	\item[Code:] All our code comes with a README, standard
@@
           changes before submitting a solution. Unfortunately, the
-          proving key for the Sudoku has size 64KB (19KB after
-          compression) which is about 6 times (respectively 10 times
-          once zipped) bigger than for Euler and Pincode, and we
-          decided not to include it.
+          proving key for Sudoku is an order of magnitude bigger than
+          for Euler and Pincode (even zipped), and we decided not to
+          include it.
 
@@
 
-    \end{lstlisting}
 \end{description}
@@
         time of solution in the contract.
-
+\end{enumerate}
 	For internal messages between these contracts, they either check that
@@
 \label{section_pincode}
+
+	\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.6\textwidth]{pincode}
+	\end{figure}
 
@@
 \label{sec_three_paradigms}
-This contest has given us the opportunity to think harder about the categories of uses of \zksnarks{} on blockchains:
+We wish to conclude with some broader considerations. This contest has
+given us the opportunity to think harder about the categories of uses
+of \zksnarks{} on blockchains:
 \begin{enumerate}
@@
 
-Of course, the boundaries between these categories may be blurred, but still they are meaningful.
-The point of the first category is that the data whose existence we are verifying is inert, static, it was chosen by the verifier according to some human meaning which is completely meaningless to the contract or the blockchain.
-In the second category, the value whose existence we are verifying has a computational (i.e.
-mathematical, see Section~\ref{subsec:math_enc}) meaning, and though this computational meaning\footnote{Of course, the answers to the Project Euler problems do have computational meaning ultimately, but no program is provided to encode the problem or check the solution.
-This computational meaning is inferred from the english description of the problem by the problem solver.} is not present on the blockchain itself, it is implicitly present in the verification key.
-Finally, the third category consists in the verification of data which has blockchain-protocol-level computational meaning (such as a public key).
-The privacy aspect of \zksnarks{}, which is of course the whole point, had initially hidden these distinctions from us.
+Of course, the boundaries between these categories may be blurred, but
+still they are meaningful. The point of the first category is that the
+data whose existence we are verifying is inert, static, it was chosen
+by the verifier according to some human meaning which is completely
+meaningless to the contract or the blockchain. In the second category,
+the value whose existence we are verifying has a computational
+(i.e. mathematical, see Section~\ref{subsec:math_enc}) meaning, and
+though this computational meaning\footnote{Of course, the answers to
+  the Project Euler problems do have computational meaning ultimately,
+  but no program is provided to encode the problem or check the
+  solution. This computational meaning is inferred from the english
+  description of the problem by the problem solver.} is not present on
+the blockchain itself, it is implicitly present in the verification
+key. Finally, the third category consists in the verification of data
+which has blockchain-protocol-level computational meaning (such as a
+public key). The privacy aspect of \zksnarks{}, which is of course the
+whole point, had initially hidden these distinctions from us.
 
-In category 1, the main advantage of \zksnarks{} is to not spoil the fun for other competitors.
-One must protect oneself from replay attacks (re-using the same zero-knowledge proof as some other competitor in order to pretend one has solved the problem) and brute-forcing the answer.
+In category 1, the main advantage of \zksnarks{} is to not spoil the
+fun for other competitors. One must protect oneself from replay
+attacks (re-using the same zero-knowledge proof as some other
+competitor in order to pretend one has solved the problem) and
+brute-forcing the answer.
 
-In category 2, the point is to guarantee some mathematical properties of a wide range of submitted solutions to a given problem of a known computational nature, when not all of possible instances may be computed in advance.
-The \emph{zero-knowledge} part may or may not be important, but the \emph{succinct} part may well save some gas for cost-heavy verifications.
+In category 2, the point is to guarantee some mathematical properties
+of a wide range of submitted solutions to a given problem of a known
+computational nature, when not all of possible instances may be
+computed in advance. The \emph{zero-knowledge} part may or may not be
+important, but the \emph{succinct} part may well save some gas for
+cost-heavy verifications.
 
-In category 3, the zero-knowledge part plays a crucial part in preventing man-in-the-middle attacks for security-critical operations such as changing a lost public key in a wallet, or sending an anonymous amount of tokens to an anonymous recipient, or voting without revealing one's ballot.
+In category 3, the zero-knowledge part plays a crucial part in
+preventing man-in-the-middle attacks for security-critical operations
+such as changing a lost public key in a wallet, or sending an
+anonymous amount of tokens to an anonymous recipient, or voting
+without revealing one's ballot.
 
-These three categories may be combined in several ways depending on the purpose.
+These three categories may be combined in several ways depending on
+the purpose.
 

### 2021-07-14 01_sudoku/tests/03_solve_sudoku.sh
remove spurious std::couts in sudoku.cpp

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+. ./env.sh
+
+$FT exec -- ../cpp/sudoku-client --sudoku-generate-proof --instance initial_instance.in --solution initial_solution.in || exit 2
+
+$FT call sudoku submit '{ "proof" : "%{file:proof.bin.hex}" }' --wait || exit 2

### 2021-07-14 01_sudoku/tests/03_solve_sudoku.sh
Finishing up scripts and READMEs

@@ -2,6 +2,14 @@
 
 . ./env.sh
 
+printf "Attempting to create a proof with instance:\n\n$(cat initial_instance.in)\n\nand solution:\n\n$(cat initial_solution.in)"
+
+sleep 4
+
 $FT exec -- ../cpp/sudoku-client --sudoku-generate-proof --instance initial_instance.in --solution initial_solution.in || exit 2
+
+cmd cp proof.bin.hex initialproof.bin.hex
+
+printf "submitting proof to smart contract..."
 
 $FT call sudoku submit '{ "proof" : "%{file:proof.bin.hex}" }' --wait || exit 2

### 2021-07-15 03_pincode/tests/01_prepare.sh
Add deployment of Pincode

@@ -2,6 +2,6 @@
 
 . ./env.sh
 
-cmd ../cpp/pincode-client prepare ${PINCODE_PASSPHRASE} || exit 2
+cmd ../cpp/pincode-client prepare "${PINCODE_PASSPHRASE}" || exit 2
 
 zip provkey.bin.zip provkey.bin || exit 2

### 2021-07-15 bin/cli/src/circuit.hpp
Edit comment

@@ -108,7 +108,8 @@ private:
                             hash_msg_block,
                             blueprint_variable_vector<FieldType>(1, secret_hash));
         
-        // The voters set may contain zeros if there is less than maximum voters.
+        // In case the voters list contains less than the maximum amount possible
+        // we fill the rest with zeros.
         // So we have to make sure the secret's hash is not zero.
         blueprint_variable_vector<FieldType> secret_hash_bits;
         secret_hash_bits.allocate(bp, modulus_bits);

### 2021-07-15 02_euler/tests/04_new_user.sh
add deployments for 01 and 02

@@ -2,7 +2,7 @@
 
 . ./env.sh
 
-$FT multisig transfer 1 --from user1 --to EulerRoot new_user '{ "pubkey": "0x%{account:pubkey:user1}" }' --wait || exit 2
+$FT multisig transfer 5 --from user1 --to EulerRoot new_user '{ "pubkey": "0x%{account:pubkey:user1}" }' --wait || exit 2
 
 rm -f user.addr
 $FT call --local EulerRoot user_address '{ "pubkey": "0x%{account:pubkey:user1}" }' --subst @%{res:addr} --output user.addr || exit 2

### 2021-07-15 02_euler/tests/05_submit_user1.sh

@@ -4,9 +4,9 @@
 
 cmd ../cpp/euler-client prove ${EULER_PROBLEM} ${EULER_NONCE} ${EULER_SOLUTION} $($FT output '%{account:pubkey:user1}') || exit 2
 
+$FT call euler_user submit '{ "problem": %{env:EULER_PROBLEM}, "proof": "%{file:proof.bin.hex}" }' --wait --sign user1 || exit 2
 
+# $FT multisig transfer 1 --from user1 --to EulerRoot submit '{ "problem": %{env:EULER_PROBLEM}, "proof": "%{file:proof.bin.hex}", "pubkey": "0x%{account:pubkey:user1}" }' --wait || exit 2
 
-$FT multisig transfer 1 --from user1 --to EulerRoot submit '{ "problem": %{env:EULER_PROBLEM}, "proof": "%{file:proof.bin.hex}", "pubkey": "0x%{account:pubkey:user1}" }' --wait || exit 2
-
-$FT call --local euler_user get    
-$FT call --local euler_problem get    
+$FT call --local euler_user get
+$FT call --local euler_problem get

### 2021-07-15 01_sudoku/cpp/sudoku.cpp
Fix sudoku includes

@@ -1,7 +1,7 @@
 #include <stdlib.h>
 #include <iostream>
 
-#include <nil/crypto3/zk/snark/blueprint.hpp>
+#include <nil/crypto3/zk/components/blueprint.hpp>
 #include <nil/crypto3/zk/snark/algorithms/generate.hpp>
 #include <nil/crypto3/zk/snark/algorithms/verify.hpp>
 #include <nil/crypto3/zk/snark/algorithms/prove.hpp>

### 2021-07-15 01_sudoku/cpp/sudoku.hpp

@@ -26,20 +26,23 @@
 #ifndef CRYPTO3_BLUEPRINT_SUDOKU_TEST_COMPONENT_HPP
 #define CRYPTO3_BLUEPRINT_SUDOKU_TEST_COMPONENT_HPP
 
-#include <nil/crypto3/zk/snark/component.hpp>
+#include <nil/crypto3/zk/components/component.hpp>
 
-#include <nil/crypto3/zk/snark/blueprint.hpp>
-#include <nil/crypto3/zk/snark/blueprint_variable.hpp>
-#include <nil/crypto3/zk/snark/components/basic_components.hpp>
+#include <nil/crypto3/zk/components/blueprint.hpp>
+#include <nil/crypto3/zk/components/blueprint_variable.hpp>
+// #include <nil/crypto3/zk/snark/components/basic_components.hpp>
 
 #include <nil/crypto3/zk/snark/relations/constraint_satisfaction_problems/r1cs.hpp>
 
-using namespace nil::crypto3::zk::snark;
+
 using namespace nil::crypto3;
-// using namespace nil::crypto3::algebra;
+using namespace nil::crypto3::zk;
+using namespace nil::crypto3::zk::components;
+using namespace nil::crypto3::algebra;
+using namespace nil::crypto3::zk::snark;
 
 template<typename FieldType>
-class test_component : public nil::crypto3::zk::snark::components::component<FieldType> {
+class test_component : public nil::crypto3::zk::components::component<FieldType> {
     using field_type = FieldType;
     //private (intermediary) variables
 
@@ -196,7 +199,7 @@ public:
                 //const blueprint_variable<field_type> &out,
                 //const blueprint_variable<field_type> &x
  ) :
[…]

### 2021-07-15 01_sudoku/ml/freeton_sudoku_generator/scripts/after.sh
remove useless ml code for submission

@@ -1,11 +1,0 @@
-#!/bin/sh
-
-# Read more on this file in before.sh
-
-COMMAND=$1
-shift
-SCRIPT=./scripts/after-${COMMAND}.sh
-
-if [ -e ${SCRIPT} ]; then
-   exec ${SCRIPT} $*
-fi

### 2021-07-15 01_sudoku/ml/freeton_sudoku_generator/scripts/before.sh

@@ -1,29 +1,0 @@
-#!/bin/sh
-
-# This script and after.sh are used to mimic drom hooks from the Makefile
-# and opam file.
-# drom calls the following hooks:
-#  * before-build.sh [PACKAGE] (PACKAGE only provided if called from opam for PACKAGE.opam)
-#  * after-build.sh  [PACKAGE]
-#  * before-sphinx.sh SPHINX_TARGET
-#  * after-sphinx.sh SPHINX_TARGET
-#  * before-odoc.sh ODOC_TARGET
-#  * after-odoc.sh ODOC_TARGET
-#  * before-test.sh
-#  * after-test.sh
-#  * before-install.sh PACKAGE
-#  * after-clean.sh
-#  * after-distclean.sh
-#  * before-fmt.sh
-#  * after-fmt.sh
-#  * before-run.sh CMD ARGS
-#  * before-publish.sh OPAM_REPO
-#  * after-publish.sh OPAM_REPO
-
-COMMAND=$1
-shift
-SCRIPT=./scripts/before-${COMMAND}.sh
-
-if [ -e ${SCRIPT} ]; then
-   exec ${SCRIPT} $*
-fi

### 2021-07-15 01_sudoku/ml/freeton_sudoku_generator/sphinx/conf.py

@@ -1,223 +1,0 @@
-#!/usr/bin/env python3
-# -*- coding: utf-8 -*-
-#
-# sudoku_generator documentation build configuration file, created by
-# sphinx-quickstart.
-#
-# This file is execfile()d with the current directory set to its
-# containing dir.
-#
-# Note that not all possible configuration values are present in this
-# autogenerated file.
-#
-# All configuration values have a default; values that are commented out
-# serve to show the default.
-
-# If extensions (or modules to document with autodoc) are in another directory,
-# add these directories to sys.path here. If the directory is relative to the
-# documentation root, use os.path.abspath to make it absolute, like shown here.
-#
-# sys.path.insert(0, os.path.abspath('.'))
-
-import os
-import sys
-import datetime
-import subprocess
-from os import environ
-sys.path.insert(0, os.path.abspath('.') + '/_extensions')
-
-# -- General configuration ------------------------------------------------
-
-# If your documentation needs a minimal Sphinx version, state it here.
-#
-# needs_sphinx = '1.0'
-
-# Add any Sphinx extension module names here, as strings. They can be
-# extensions coming with Sphinx (named 'sphinx.ext.*') or your custom
-# ones.
-#extensions = ['sphinx.ext.extlinks']
-
-# Add any paths that contain templates here, relative to this directory.
-templates_path = ['_templates']
-
-# The suffix(es) of source filenames.
-# You can specify multiple suffix as a list of string:
-#
-source_suffix = ['.rst', '.md']
-# source_suffix = '.rst'
-
-# The master toctree document.
-master_doc = 'index'
-
-# General information about the project.
-project = 'sudoku_generator'
-copyright = 'TS <ts@noemailsplease.com>'
-author = 'TS <ts@noemailsplease.com>'
-
-# The version info for the project you're documenting, acts as replacement for
-# |version| and |release|, also used in various other places throughout the
-# built documents.
-#
-# The short X.Y version.
-
-git = subprocess.check_output("git describe --always", shell=True).decode("utf-8")
-branch= subprocess.check_output("git rev-parse --abbrev-ref HEAD", shell=True).decode("utf-8")
-version = branch + " (" + git + ")"
-# version = os.environ.get('CI_COMMIT_REF_NAME', 'v1.0')
-# The full version, including alpha/beta/rc tags.
-release = version + datetime.datetime.now().strftime(" (%Y/%m/%d %H:%M)")
[…]

### 2021-07-15 01_sudoku/ml/freeton_sudoku_generator/src/sudoku_generator/main.cpp

@@ -1,144 +1,0 @@
-//---------------------------------------------------------------------------//
-// Copyright (c) 2018-2021 Mikhail Komarov <nemo@nil.foundation>
-//
-// Licensed under the Apache License, Version 2.0 (the "License");
-// you may not use this file except in compliance with the License.
-// You may obtain a copy of the License at
-//
-//    http://www.apache.org/licenses/LICENSE-2.0
-//
-// Unless required by applicable law or agreed to in writing, software
-// distributed under the License is distributed on an "AS IS" BASIS,
-// WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
-// See the License for the specific language governing permissions and
-// limitations under the License.
-//---------------------------------------------------------------------------//
-
-#include <iostream>
-
-#include <boost/filesystem.hpp>
-#include <boost/program_options.hpp>
-
-#include "detail/r1cs_examples.hpp"
-#include "detail/sha256_component.hpp"
-
-#include <nil/crypto3/algebra/curves/bls12.hpp>
-#include <nil/crypto3/algebra/fields/bls12/base_field.hpp>
-#include <nil/crypto3/algebra/fields/bls12/scalar_field.hpp>
-#include <nil/crypto3/algebra/fields/arithmetic_params/bls12.hpp>
-#include <nil/crypto3/algebra/curves/params/multiexp/bls12.hpp>
-#include <nil/crypto3/algebra/curves/params/wnaf/bls12.hpp>
-
-#include <nil/crypto3/zk/snark/blueprint.hpp>
-#include <nil/crypto3/zk/snark/blueprint_variable.hpp>
-
-#include <nil/crypto3/zk/snark/schemes/ppzksnark/r1cs_gg_ppzksnark.hpp>
-#include <nil/crypto3/zk/snark/schemes/ppzksnark/r1cs_gg_ppzksnark/marshalling.hpp>
-
-#include <nil/crypto3/zk/snark/algorithms/generate.hpp>
-#include <nil/crypto3/zk/snark/algorithms/verify.hpp>
-#include <nil/crypto3/zk/snark/algorithms/prove.hpp>
-
-#include "toto.cpp"
-
-using namespace nil::crypto3;
-
-typedef algebra::curves::bls12<381> curve_type;
-typedef typename curve_type::scalar_field_type field_type;
-
-typedef zk::snark::r1cs_gg_ppzksnark<curve_type> scheme_type;
-
-
-
[…]

### 2021-07-15 01_sudoku/ml/freeton_sudoku_generator/sudoku.cpp

@@ -1,229 +1,0 @@
-#include <stdlib.h>
-#include <iostream>
-
-#include <nil/crypto3/zk/snark/blueprint.hpp>
-#include <nil/crypto3/zk/snark/algorithms/generate.hpp>
-#include <nil/crypto3/zk/snark/algorithms/verify.hpp>
-#include <nil/crypto3/zk/snark/algorithms/prove.hpp>
-
-#include <nil/crypto3/zk/snark/schemes/ppzksnark/r1cs_gg_ppzksnark.hpp>
-
-#include <nil/crypto3/algebra/curves/bls12.hpp>
-#include <nil/crypto3/algebra/fields/bls12/base_field.hpp>
-#include <nil/crypto3/algebra/fields/bls12/scalar_field.hpp>
-#include <nil/crypto3/algebra/fields/arithmetic_params/bls12.hpp>
-#include <nil/crypto3/algebra/curves/params/multiexp/bls12.hpp>
-#include <nil/crypto3/algebra/curves/params/wnaf/bls12.hpp>
-
-#include <nil/crypto3/algebra/fields/detail/element/fp.hpp>
-#include <nil/crypto3/algebra/fields/detail/element/fp2.hpp>
-
-#include "sudoku.hpp"
-
-using namespace nil::crypto3::zk::snark;
-using namespace nil::crypto3::algebra;
-
-int test(){
-
-    using curve_type = curves::bls12<381>;
-    using field_type = typename curve_type::scalar_field_type;
-
-    // Create blueprint
-
-    blueprint<field_type> bp;
-    //private (intermediary) variables
-
-    blueprint_variable<field_type> x_0_0;
-    blueprint_variable<field_type> x_0_1;
-    blueprint_variable<field_type> x_0_2;
-    blueprint_variable<field_type> x_0_3;
-    blueprint_variable<field_type> x_1_0;
-    blueprint_variable<field_type> x_1_1;
-    blueprint_variable<field_type> x_1_2;
-    blueprint_variable<field_type> x_1_3;
-    blueprint_variable<field_type> x_2_0;
-    blueprint_variable<field_type> x_2_1;
-    blueprint_variable<field_type> x_2_2;
-    blueprint_variable<field_type> x_2_3;
-    blueprint_variable<field_type> x_3_0;
-    blueprint_variable<field_type> x_3_1;
-    blueprint_variable<field_type> x_3_2;
[…]

### 2021-07-15 01_sudoku/ml/freeton_sudoku_generator/sudoku.hpp

@@ -1,475 +1,0 @@
-//---------------------------------------------------------------------------//
-// Copyright (c) 2018-2021 Mikhail Komarov <nemo@nil.foundation>
-// Copyright (c) 2020-2021 Nikita Kaskov <nbering@nil.foundation>
-//
-// MIT License
-//
-// Permission is hereby granted, free of charge, to any person obtaining a copy
-// of this software and associated documentation files (the "Software"), to deal
-// in the Software without restriction, including without limitation the rights
-// to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
-// copies of the Software, and to permit persons to whom the Software is
-// furnished to do so, subject to the following conditions:
-//
-// The above copyright notice and this permission notice shall be included in all
-// copies or substantial portions of the Software.
-//
-// THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
-// IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
-// FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
-// AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
-// LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
-// OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
-// SOFTWARE.
-//---------------------------------------------------------------------------//
-
-#ifndef CRYPTO3_BLUEPRINT_SUDOKU_TEST_COMPONENT_HPP
-#define CRYPTO3_BLUEPRINT_SUDOKU_TEST_COMPONENT_HPP
-
-#include <nil/crypto3/zk/snark/component.hpp>
-
-#include <nil/crypto3/zk/snark/blueprint.hpp>
-#include <nil/crypto3/zk/snark/blueprint_variable.hpp>
-#include <nil/crypto3/zk/snark/components/basic_components.hpp>
-
-#include <nil/crypto3/zk/snark/relations/constraint_satisfaction_problems/r1cs.hpp>
-
-using namespace nil::crypto3::zk::snark;
-// using namespace nil::crypto3::algebra;
-
-template<typename FieldType>
[…]

### 2021-10-03 src/Server.Business/Requests/SendSubscriptionAddClientInfoFilter.cs
feat(Server) skip publishing for message without client info in db

@@ -1,17 +1,19 @@
-﻿using System;
-using System.Threading.Tasks;
+﻿using System.Threading.Tasks;
 using GreenPipes;
 using MassTransit;
+using Microsoft.Extensions.Logging;
 
 namespace Server.Requests
 {
     public class SendSubscriptionAddClientInfoFilter<T> : IFilter<PublishContext<T>> where T : class
     {
+        private readonly ILogger<SendSubscriptionAddClientInfoFilter<T>> _logger;
         private readonly ServerDbContext _serverContext;
 
-        public SendSubscriptionAddClientInfoFilter(ServerDbContext serverContext)
+        public SendSubscriptionAddClientInfoFilter(ServerDbContext serverContext, ILogger<SendSubscriptionAddClientInfoFilter<T>> logger)
         {
             _serverContext = serverContext;
+            _logger = logger;
         }
 
         public async Task Send(PublishContext<T> context, IPipe<PublishContext<T>> next)
@@ -21,11 +23,19 @@ namespace Server.Requests
                 var cancellationToken = context.CancellationToken;
 
                 var clientInfo = await _serverContext.ClientInfos.FindAsync(new object[] { message.Hash }, cancellationToken);
-                if (clientInfo == null) throw new NullReferenceException("Client not found") { Data = { { "ClientHash", message.Hash } } };
-                context.Headers.Set("clientInfo", clientInfo);
-            }
+                if (clientInfo == null)
+                {
+                    _logger.LogWarning("Client {ClientHash} not found in the Database, skip publishing..", message.Hash);
+                    return;
+                }
 
-            await next.Send(context);
+                context.Headers.Set("clientInfo", clientInfo);
+                await next.Send(context);
+            }
+            else
+            {
+                await next.Send(context);
+            }
         }
 
         public void Probe(ProbeContext context)

### 2021-10-03 src/Server/Startup.cs
refactor(Client) rename constants and use everywhere

@@ -30,14 +30,14 @@ namespace Server
             // configure asp net
             services.AddControllersWithViews(options => { options.InputFormatters.Insert(options.InputFormatters.Count, new TextPlainInputFormatter()); });
             services.AddRazorPages();
-            services.AddSwaggerDocument(settings => { settings.Title = ProjectConstants.AppName; });
+            services.AddSwaggerDocument(settings => { settings.Title = ProjectConstants.ServiceName; });
             services.Configure<RouteOptions>(options => options.LowercaseUrls = true);
             services.AddCors(o => o.AddPolicy("SubmitClient", builder => builder.AllowAnyOrigin()));
 
             // add configuration options
             services.ConfigureOptions(Configuration);
 
-            // http client to sent http hooks
+            // http client for sending http hooks
             services.AddHttpClient();
 
             // add masstransit with rabbit if configured else use in-memory bus

### 2021-10-03 src/Shared/ProjectConstants.cs

@@ -5,6 +5,9 @@
         public const string ServerUrl = "https://notify-contest.ddns.net/";
         public const string GitHubLink = "https://github.com/ton-actions/free-ton-http-notification-provider";
         public const string TelegramLink = "https://t.me/ton_actions_chat";
-        public const string AppName = "Free TON Notify";
+        public const string ServiceName = "Free TON Notify";
+
+        public const string ServiceDescription =
+            "This is a notification provider. It can catch messages from the blockchain and send them to various endpoints.";
     }
 }

### 2021-10-03 src/Client.Storage/MessageInfoStorage.cs
refactor(Client.Storage) change storage key separator

@@ -10,7 +10,7 @@ namespace Client.Storage
     public class MessageInfoStorage : ConcurrentEntityStorageBase<List<MessageInfo>>, IMessageInfoStorage
     {
         public MessageInfoStorage(ILocalStorageService localStorage, NavigationManager navigationManager) : base(localStorage,
-            $"MessageInfos_{GetClientHash(navigationManager)}")
+            $"MessageInfos:{GetClientHash(navigationManager)}")
         {
         }
 

### 2021-10-03 scripts/setup-github-actions.sh
attempt to fix actions

@@ -1,9 +1,9 @@
 #!/bin/bash
 # You can safely delete this file after you've setup your docker repo in .github/workflows/latest.yml
 
-project_name="docker-express-typescript-boilerplate"
+project_name="free-ton-notifications-service"
 filename=".github/workflows/latest.yml"
-default_repo="sidhantpanda/docker-express-typescript-boilerplate/docker-express-typescript-boilerplate"
+default_repo="Strafi/free-ton-notifications-service/free-ton-notifications-service"
 
 configure_github_actions() {
   read -p "Enter your Github username: "  github_user

### 2021-10-03 src/app.ts

@@ -5,6 +5,7 @@ import express, { Request, Response, NextFunction } from 'express';
 import ApplicationError from './errors/application-error';
 import routes from './routes';
 import logger from './logger';
+import './lib/kafka-client';
 
 const app = express();
 

### 2021-10-03 src/controllers/webhook/subscribe.ts

@@ -1,0 +1,30 @@
+import { Request, RequestHandler } from 'express';
+import Joi from '@hapi/joi';
+import { v1 as uuidv1 } from 'uuid';
+import requestMiddleware from '../../middleware/request-middleware';
+import WebhookConsumer from '../../models/WebhookConsumer';
+
+export const subscribeSchema = Joi.object().keys({
+	data: Joi.string().required()
+});
+
+interface SubscribeReqBody {
+	data: string;
+	hash: string;
+}
+
+const subscribe: RequestHandler = async (req: Request<{}, {}, SubscribeReqBody>, res) => {
+	const { data: endpoint, hash } = req.body;
+	const uuid = uuidv1();
+
+	const consumer = new WebhookConsumer({ uuid, endpoint, hash });
+	await consumer.save();
+
+	res.send({
+		message: 'Include the uuid in webhook response to verify that you have an access to the requested url',
+		url: consumer.endpoint,
+		uuid: consumer.uuid
+	});
+};
+
+export default requestMiddleware(subscribe, { validation: { body: subscribeSchema } });

### 2021-10-03 src/controllers/webhook/unsubscribe.ts

@@ -1,0 +1,32 @@
+import { Request, RequestHandler } from 'express';
+import Joi from '@hapi/joi';
+import requestMiddleware from '../../middleware/request-middleware';
+import WebhookConsumer from '../../models/WebhookConsumer';
+
+export const unsubscribeSchema = Joi.object().keys({
+	uuid: Joi.string().required()
+});
+
+interface UnsubscribeReqBody {
+	uuid: string;
+}
+
+const unsubscribe: RequestHandler = async (req: Request<{}, {}, UnsubscribeReqBody>, res) => {
+	const { uuid } = req.body;
+
+	const consumer = await WebhookConsumer.findOne({ uuid });
+
+	if (!consumer) {
+		return res.status(404).send({
+			error: `No consumer with uuid: ${uuid}`
+		});
+	}
+
+	await consumer.delete();
+
+	return res.send({
+		message: 'Unsubscribed'
+	});
+};
+
+export default requestMiddleware(unsubscribe, { validation: { body: unsubscribeSchema } });

### 2021-10-03 src/lib/kafka-client.ts

@@ -1,0 +1,34 @@
+import { Kafka } from 'kafkajs';
+
+const kafka = new Kafka({
+	clientId: 'i4ins-kafka-client',
+	brokers: [process.env.KAFKA_BROKER],
+	sasl: {
+		mechanism: 'scram-sha-512',
+		username: process.env.KAFKA_USERNAME,
+		password: process.env.KAFKA_PASSWORD
+	}
+});
+
+export const consumer = kafka.consumer({ groupId: 'i4ins-notifications-consumer' });
+
+const run = async () => {
+	await consumer.connect();
+	await consumer.subscribe({ topic: 'notifications-7', fromBeginning: true });
+
+	await consumer.run({
+		eachMessage: async ({ topic, partition, message }) => {
+			console.log(topic);
+
+			console.log({
+				partition,
+				offset: message.offset,
+				value: message.value.toString()
+			});
+		}
+	});
+};
+
+run().catch(err => console.error(err));
+
+export default kafka;

### 2021-10-03 src/models/WebhookConsumer.ts

@@ -1,0 +1,36 @@
+import { Model, Schema, model } from 'mongoose';
+import TimeStampPlugin, { ITimeStampedDocument } from './plugins/timestamp-plugin';
+
+export interface IWebhookConsumer extends ITimeStampedDocument {
+	uuid: string;
+	endpoint: string;
+	hash?: string;
+}
+
+interface IWebhookConsumerModel extends Model<IWebhookConsumer> { }
+
+const schema = new Schema<IWebhookConsumer>({
+	uuid: {
+		type: String,
+		index: true,
+		required: true,
+		unique: true
+	},
+	endpoint: {
+		type: String,
+		index: true,
+		required: true,
+		unique: true
+	},
+	hash: {
+		type: String,
+		index: true,
+		unique: true
+	}
+});
+
+schema.plugin(TimeStampPlugin);
+
+const WebhookConsumer: IWebhookConsumerModel = model<IWebhookConsumer, IWebhookConsumerModel>('WebhookConsumer', schema);
+
+export default WebhookConsumer;

### 2021-10-03 src/routes.ts

@@ -1,24 +1,19 @@
 import { Router } from 'express';
 import swaggerUi from 'swagger-ui-express';
 import apiSpec from '../openapi.json';
-
-import * as BookController from './controllers/book';
-
-const swaggerUiOptions = {
-	customCss: '.swagger-ui .topbar { display: none }'
-};
+import * as WebhookController from './controllers/webhook';
 
 const router = Router();
 
-// Book routes
-router.post('/book/add', BookController.add);
-router.get('/book/all', BookController.all);
-router.get('/book/:bookId', BookController.get);
-router.delete('/book/:bookId', BookController.remove);
-router.get('/book/search', BookController.search);
+// Webhook routes
+router.post('/webhook/subscribe', WebhookController.subscribe);
 
 // Dev routes
 if (process.env.NODE_ENV === 'development') {
+	const swaggerUiOptions = {
+		customCss: '.swagger-ui .topbar { display: none }'
+	};
+
 	router.use('/dev/api-docs', swaggerUi.serve);
 	router.get('/dev/api-docs', swaggerUi.setup(apiSpec, swaggerUiOptions));
 }

### 2021-10-03 scripts/setup-github-actions.sh
new github actions, add module info endpoint

@@ -1,17 +1,0 @@
-#!/bin/bash
-# You can safely delete this file after you've setup your docker repo in .github/workflows/latest.yml
-
-project_name="free-ton-notifications-service"
-filename=".github/workflows/latest.yml"
-default_repo="Strafi/free-ton-notifications-service/free-ton-notifications-service"
-
-configure_github_actions() {
-  read -p "Enter your Github username: "  github_user
-  read -p "Enter this app's Github repo name: "  project_name
-
-  docker_repo="$github_user/$project_name/$project_name"
-  sed -i '' "s+$default_repo+$docker_repo+g" $filename
-  echo "Configured Github Docker Repo to: ${docker_repo}"
-}
-
-configure_github_actions

### 2021-10-03 src/constants/index.ts

@@ -1,0 +1,5 @@
+import ROUTES from './routes';
+
+export {
+	ROUTES
+};

### 2021-10-03 src/constants/routes.ts

@@ -1,0 +1,13 @@
+const WEBHOOK_ROOT = '/webhook';
+const INFO_ROOT = '/info';
+
+const ROUTES = {
+	WEBHOOK: {
+		SUBSCRIBE: `${WEBHOOK_ROOT}/subscribe`
+	},
+	INFO: {
+		GET: `${INFO_ROOT}/get`
+	}
+};
+
+export default ROUTES;

### 2021-10-03 src/routes.ts

@@ -1,12 +1,17 @@
 import { Router } from 'express';
 import swaggerUi from 'swagger-ui-express';
 import apiSpec from '../openapi.json';
+import ROUTES from './constants/routes';
 import * as WebhookController from './controllers/webhook';
+import * as InfoController from './controllers/info';
 
 const router = Router();
 
 // Webhook routes
-router.post('/webhook/subscribe', WebhookController.subscribe);
+router.post(ROUTES.WEBHOOK.SUBSCRIBE, WebhookController.subscribe);
+
+// Info routes
+router.post(ROUTES.INFO.GET, InfoController.get);
 
 // Dev routes
 if (process.env.NODE_ENV === 'development') {

### 2021-10-03 src/Client.Storage/IMessageInfoStorage.cs
feat(Client.Storage) impl init method to create empty entity

@@ -5,8 +5,9 @@ namespace Client.Storage
 {
     public interface IMessageInfoStorage
     {
+        Task Init();
         Task<IReadOnlyCollection<MessageInfo>> GetAll();
         Task<IReadOnlyCollection<MessageInfo>> Push(MessageInfo messageInfo);
-        Task ClearAll();
+        Task Clear();
     }
 }

### 2021-10-03 src/Client.Storage/MessageInfoStorage.cs

@@ -9,9 +9,16 @@ namespace Client.Storage
 {
     public class MessageInfoStorage : ConcurrentEntityStorageBase<List<MessageInfo>>, IMessageInfoStorage
     {
+        public const string StoragePrefix = "MessageInfos";
+
         public MessageInfoStorage(ILocalStorageService localStorage, NavigationManager navigationManager) : base(localStorage,
-            $"MessageInfos:{GetClientHash(navigationManager)}")
+            $"{StoragePrefix}:{GetClientHash(navigationManager)}")
         {
+        }
+
+        public async Task Init()
+        {
+            await Update(_ => { });
         }
 
         public async Task<IReadOnlyCollection<MessageInfo>> GetAll()
@@ -23,12 +30,13 @@ namespace Client.Storage
         {
             return await Update(list =>
             {
-                list.Insert(0, messageInfo);
+                if (!list.Exists(info => info.Message == messageInfo.Message))
+                    list.Insert(0, messageInfo);
                 return list;
             });
         }
 
-        public async Task ClearAll()
+        public async Task Clear()
         {
             await Update(list => { list.Clear(); });
         }

### 2021-10-03 src/Server.MassTransit/ServiceCollectionExtensions.cs
feat(Server) export MT metrics

@@ -1,4 +1,5 @@
 ﻿using MassTransit;
+using MassTransit.PrometheusIntegration;
 using MassTransit.RabbitMqTransport;
 using MassTransit.Registration;
 using MassTransit.SignalR;
@@ -31,18 +32,26 @@ namespace Server
                     if (useRabbitMq)
                         x.UsingRabbitMq((context, cfg) =>
                         {
-                            cfg.UsePublishFilter(typeof(SendSubscriptionAddClientInfoFilter<>), context);
-
                             SetupRabbitMqHost(cfg, context);
-
+                            ConfigureContext(cfg, context);
                             cfg.ConfigureEndpoints(context);
                         });
                     else
-                        x.UsingInMemory((context, cfg) => cfg.ConfigureEndpoints(context));
+                        x.UsingInMemory((context, cfg) =>
+                        {
+                            ConfigureContext(cfg, context);
+                            cfg.ConfigureEndpoints(context);
+                        });
                 })
                 .AddMassTransitHostedService();
 
             return services;
+        }
+
+        private static void ConfigureContext(IBusFactoryConfigurator cfg, IConfigurationServiceProvider context)
+        {
+            cfg.UsePublishFilter(typeof(SendSubscriptionAddClientInfoFilter<>), context);
+            cfg.UsePrometheusMetrics();
         }
 
         private static void SetupRabbitMqHost(IRabbitMqBusFactoryConfigurator cfg, IConfigurationServiceProvider context)

### 2021-10-03 src/Common/ProjectConstants.cs
rename Shared to Common

@@ -1,4 +1,4 @@
-﻿namespace Shared
+﻿namespace Common
 {
     public static class ProjectConstants
     {
@@ -9,5 +9,7 @@
 
         public const string ServiceDescription =
             "This is a notification provider. It can catch messages from the blockchain and send them to various endpoints.";
+
+        public const string DeBotLink = "https://web.ton.surf/debot?address=0%3A433f7b97e4e613397175a2d9d1094643b5b90d1f095c423997f95fbf905a3ae3&net=devnet";
     }
 }

### 2021-10-03 src/Server.Business/Requests/SubmitClientConsumer.cs

@@ -1,11 +1,11 @@
 ﻿using System;
 using System.Threading;
 using System.Threading.Tasks;
+using Common;
 using Flurl;
 using MassTransit;
 using Microsoft.Extensions.Configuration;
 using Microsoft.Extensions.Logging;
-using Shared;
 
 namespace Server.Requests
 {

### 2021-10-03 src/Server/Startup.cs

@@ -1,4 +1,5 @@
 using System;
+using Common;
 using Microsoft.AspNetCore.Builder;
 using Microsoft.AspNetCore.Diagnostics.HealthChecks;
 using Microsoft.AspNetCore.Hosting;
@@ -10,7 +11,6 @@ using Microsoft.Extensions.Hosting;
 using NSwag;
 using Prometheus;
 using Serilog;
-using Shared;
 
 namespace Server
 {

### 2021-10-04 src/Server/Controllers/EndpointController.cs
fix(Server.EndpointController) allow empty string

@@ -76,7 +76,7 @@ namespace Server.Controllers
         {
             [Required(AllowEmptyStrings = false)] public string Hash { get; init; }
 
-            [Required(AllowEmptyStrings = false)] public string Data { get; init; }
+            [Required(AllowEmptyStrings = true)] public string Data { get; init; }
         }
     }
 }

### 2021-10-04 src/Server.Business/Requests/SubmitClientConsumer.cs
cleanup(SubmitClientConsumer)

@@ -27,15 +27,13 @@ namespace Server.Requests
             var cancellationToken = context.CancellationToken;
             var hash = context.Message.Hash;
             var endpoint = context.Message.Endpoint;
-            const string serviceUrl = ProjectConstants.ServerUrl;
-            var testConsumerUrl = Url.Combine(serviceUrl, "test-consumer");
 
-            if (await ComingSoon(context)) return;
-            if (await DontAllowUseServerUrl(context, endpoint, serviceUrl)) return;
-            endpoint = GenerateEndpointIfTestCommand(endpoint, testConsumerUrl, hash);
-            if (await EndpointValidationError(context, endpoint)) return;
+            if (!endpoint.Equals("test") && await ComingSoon(context)) return;
+            if (await DontAllowUseServerUrl(context)) return;
+            GenerateEndpointIfTestCommand(hash, ref endpoint);
+            if (await EndpointValidationError(context)) return;
             await AddOrUpdateClientInfoToDb(hash, endpoint, cancellationToken);
-            await context.RespondAsync<SubmitClientSuccess>(new { Endpoint = endpoint, IsTest = true });
+            await context.RespondAsync<SubmitClientSuccess>(new { Endpoint = endpoint });
         }
 
         private async Task AddOrUpdateClientInfoToDb(string hash, string endpoint, CancellationToken cancellationToken)
@@ -57,30 +55,28 @@ namespace Server.Requests
             await _serverDbContext.SaveChangesAsync(cancellationToken);
         }
 
-        private static string GenerateEndpointIfTestCommand(string endpoint, string testConsumerUrl, string hash)
+        private static void GenerateEndpointIfTestCommand(string hash, ref string endpoint)
         {
-            return endpoint.Equals("test", StringComparison.OrdinalIgnoreCase)
-                ? Url.Combine(testConsumerUrl, hash[..12])
-                : endpoint;
+            if (endpoint.Equals("test", StringComparison.OrdinalIgnoreCase))
+                endpoint = Url.Combine(ProjectConstants.ServerUrl, "test-consumer", hash[..12]);
         }
 
-        private static async Task<bool> EndpointValidationError(ConsumeContext context, string endpoint)
+        private static async Task<bool> EndpointValidationError(ConsumeContext<SubmitClient> context)
         {
-            if (EndpointValidationHelper.IsHttpEndpoint(endpoint)) return false;
[…]

### 2021-10-04 src/Server.Business/Requests/SendSubscriptionHttpConsumerDefinition.cs
feat(SendSubscriptionHttpConsumer) UseDelayedRedelivery

@@ -1,0 +1,17 @@
+﻿using System;
+using GreenPipes;
+using MassTransit;
+using MassTransit.ConsumeConfigurators;
+using MassTransit.Definition;
+
+namespace Server.Requests
+{
+    public class SendSubscriptionHttpConsumerDefinition : ConsumerDefinition<SendSubscriptionHttpConsumer>
+    {
+        protected override void ConfigureConsumer(IReceiveEndpointConfigurator endpointConfigurator,
+            IConsumerConfigurator<SendSubscriptionHttpConsumer> e)
+        {
+            e.UseDelayedRedelivery(configurator => configurator.Interval(144, TimeSpan.FromMinutes(10)));
+        }
+    }
+}

### 2021-10-04 src/Server.MassTransit/ServiceCollectionExtensions.cs

@@ -24,7 +24,8 @@ namespace Server
                 })
                 .AddMassTransit(x =>
                 {
-                    x.AddConsumer<SendSubscriptionHttpConsumer>();
+                    x.AddDelayedMessageScheduler();
+                    x.AddConsumer<SendSubscriptionHttpConsumer, SendSubscriptionHttpConsumerDefinition>();
                     x.AddRider(RiderRegistrationConfiguratorExtensions.UsingKafka);
                     x.AddSignalRHub<SignalRHub>();
                     x.SetKebabCaseEndpointNameFormatter();
@@ -50,6 +51,7 @@ namespace Server
 
         private static void ConfigureContext(IBusFactoryConfigurator cfg, IConfigurationServiceProvider context)
         {
+            cfg.UseDelayedMessageScheduler();
             cfg.UsePublishFilter(typeof(SendSubscriptionAddClientInfoFilter<>), context);
             cfg.UsePrometheusMetrics();
         }

### 2021-10-04 src/Server.Business/Requests/SubmitClientConsumer.cs
fix(Server) checking endpoint format and allow empty endpoint data

@@ -29,9 +29,9 @@ namespace Server.Requests
             var endpoint = context.Message.Endpoint;
 
             if (!endpoint.Equals("test") && await ComingSoon(context)) return;
-            if (await DontAllowUseServerUrl(context)) return;
+            if (await DontAllowUseServerUrl(context, endpoint)) return;
             GenerateEndpointIfTestCommand(hash, ref endpoint);
-            if (await EndpointValidationError(context)) return;
+            if (await EndpointValidationError(context, endpoint)) return;
             await AddOrUpdateClientInfoToDb(hash, endpoint, cancellationToken);
             await context.RespondAsync<SubmitClientSuccess>(new { Endpoint = endpoint });
         }
@@ -61,16 +61,16 @@ namespace Server.Requests
                 endpoint = Url.Combine(ProjectConstants.ServerUrl, "test-consumer", hash[..12]);
         }
 
-        private static async Task<bool> EndpointValidationError(ConsumeContext<SubmitClient> context)
+        private static async Task<bool> EndpointValidationError(ConsumeContext context, string endpoint)
         {
-            if (EndpointValidationHelper.IsHttpEndpoint(context.Message.Endpoint)) return false;
+            if (EndpointValidationHelper.IsHttpEndpoint(endpoint)) return false;
             await context.RespondAsync<SubmitClientError>(new { ErrorType = SubmitClientErrorType.EndpointValidation });
             return true;
         }
 
-        private static async Task<bool> DontAllowUseServerUrl(ConsumeContext<SubmitClient> context)
+        private static async Task<bool> DontAllowUseServerUrl(ConsumeContext context, string endpoint)
         {
-            if (!context.Message.Endpoint.StartsWith(ProjectConstants.ServerUrl, StringComparison.OrdinalIgnoreCase)) return false;
+            if (!endpoint.StartsWith(ProjectConstants.ServerUrl, StringComparison.OrdinalIgnoreCase)) return false;
             await context.RespondAsync<SubmitClientError>(new { ErrorType = SubmitClientErrorType.AccessDenied });
             return true;
         }

### 2021-10-04 src/Server/Controllers/EndpointController.cs

@@ -28,7 +28,7 @@ namespace Server.Controllers
         public async Task<OkObjectResult> SubmitClient([FromForm] EndpointParameters parameters, CancellationToken cancellationToken)
         {
             var hash = parameters.Hash;
-            var endpoint = parameters.Data.FromBase64();
+            var endpoint = parameters.Data?.FromBase64() ?? string.Empty;
 
             _logger.LogTrace("Received hash: {Hash} endpoint: {Endpoint}", hash, endpoint);
 
@@ -76,7 +76,7 @@ namespace Server.Controllers
         {
             [Required(AllowEmptyStrings = false)] public string Hash { get; init; }
 
-            [Required(AllowEmptyStrings = true)] public string Data { get; init; }
+            public string Data { get; init; }
         }
     }
 }

### 2021-10-04 src/Server/Controllers/TestConsumerController.cs
cleanup(Server) cleanup using

@@ -4,7 +4,6 @@ using System.Threading.Tasks;
 using MassTransit;
 using Microsoft.AspNetCore.Mvc;
 using Microsoft.AspNetCore.SignalR;
-using Microsoft.AspNetCore.SignalR.Protocol;
 using Microsoft.Extensions.Logging;
 
 namespace Server.Controllers
